---
title: "Prophylactic Tocilizumab in Teclistamab and Talquetamab Use for Multiple Myeloma"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options:
  chunk_output_type: console
---

<style type= "text/css">

. figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{=html}
<style type= "text/css">

. figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

<meta charset="utf-8" />
<meta http-equiv="Content-Type" content="text/html; charset=utf-8" />
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(tidyverse)
library(ggplot2)
library(gtsummary)
library(labelled)
library(patchwork)
library(survival)
library(survminer)
theme_set(theme_classic())
theme_gtsummary_compact()
```

```{r load}
# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Analyses", "Janssen Teclistamab")

data <- 
  readxl::read_xlsx(
    paste0(#path, 
      here::here(), "/data/2026_analysis",
      "/JnJ_Tec_Talq_Dataset_PHI.xlsx"),
    na = c("N/A", " ", "", "NA") # "." to fix the weird encoding with non-breaking space
  ) %>% 
  `colnames<-`(str_replace(colnames(.), "^#Infection_", "infection_type_")) %>% 
  janitor::clean_names()

data <- data %>% 
  rename(date_of_infection_1 = date_of_infection_109,
         infection_severity_1 = infection_severity_severe_hospitalization_or_requiring_iv_antibiotics_108,
         date_of_infection_2 = date_of_infection_112,
         infection_severity_2 = infection_severity_severe_hospitalization_or_requiring_iv_antibiotics_111,
         date_of_infection_3 = date_of_infection_115,
         infection_severity_3 = infection_severity_severe_hospitalization_or_requiring_iv_antibiotics_114,
         date_of_infection_4 = date_of_infection_118,
         infection_severity_4 = infection_severity_severe_hospitalization_or_requiring_iv_antibiotics_117,
         inpatient_length_of_hospital_stay_days =
           if_inpatient_length_of_hospital_stay_total_days_including_all_admissions_0_if_done_outpt_with_no_admissions
         ) %>% 
  `colnames<-`(str_remove_all(colnames(.), "_bacterial_viral_fungal"))
```

```{r exploratory function}
# check_data <- function(data){
# 
#   for(i in 1:length(colnames(data))) {
# 
#     # if(class(data[[i]]) == "factor" | class(data[[i]]) == "character") {
# 
#       # print(data[i])
#       print(colnames(data[i]))
#       print(str(data[i]))
#       print(table(data[[i]]))
#     # }
# 
#   }
# }
# 
# check_data(data[4:178])
```

```{r fix name date and recode 012etc}
data1 <- data %>% 
  # General----
  mutate(mrn = as.character(mrn)) |> 
  # Fix letter case and missing
  # mutate(across(where(is.character), ~ str_replace(., "NE|ND|N/A|Not done", NA_character_))) %>%
  mutate(across(c(where(is.character),
                  -c("patient_identifier",
                     "myeloma_involved_heavy_chain_ig_g_ig_a_ig_m_ig_d_ig_e_or_blank",
                     "specific_debulking_therapy_used_prior_to_bs_ab",
                     "best_response_to_treatment_number_1_after_post_bi_te_progression",
                     "best_response_to_treatment_number_2_after_post_bi_te_progression",
                     "pathogen"
                     )),
                ~ str_to_sentence(.) )) %>%
  mutate(across(c(contains("vgpr") #"response_to_bridging_chemotherapy"
                  ),
                ~ str_to_upper(.) )) %>%
  # Recode Y/N
  mutate_at(c("tal_specifically_designed_as_pre_car_t_holding_or_bridging_y_n"
  ), 
  ~ case_when(
    . == "Y"                                              ~ "Yes",
    . == "N"                                              ~ "No",
    TRUE                                                ~ as.character(.)
  )) %>% 
  # Recode 0/1
  mutate_at(c("prophylactic_tocilizumab_n_0_y_1",
              "cerebellar_toxicity_or_ataxia_if_so_describe",
              "infection_n_0_y_1", 
              "infection_severity_1", "infection_severity_2",
              "infection_severity_3", "infection_severity_4",
              "recurrent_crs_n_0_y_1",
              "tocilizumab_as_tx_n_0_y_1", "steroid_use_as_tx_n_0_y_1", "anakinra_n_0_y_1",
              "bs_ab_combined_at_any_point_such_as_with_pom_dara_or_other_bs_ab_no_0_yes_1",
              "bs_ab_served_only_as_pre_car_t_bridging_0_no_1_yes",
              "oligo_or_non_secretory_at_bs_ab_initiation_0_no_1_yes",
              "deletion_17p_prior_to_bs_ab_0_no_1_yes", "t_4_14_prior_to_bs_ab_0_no_1_yes", 
              "t_11_14_prior_to_bs_ab_0_no_1_yes", "t_14_16_prior_to_bs_ab_0_no_1_yes", 
              "gain_amp1q21_prior_to_bs_ab_0_no_1_yes", "amp_1_q_only_0_no_1_yes",
              "deletion_1p_0_no_1_yes",
              "prior_auto_sct_no_0_yes_1",
              "prior_bcma_directed_therapy_no_0_y_1",
              "prior_cart_0_no_1_yes",
              "triple_class_refractory_i_mi_d_pi_anti_cd38_no_0_y_1",
              "penta_refractory_2_p_is_2_i_mi_ds_anti_cd38_no_0_y_1",
              "debulking_therapy_prior_to_bs_ab_no_0_y_1",
              "did_patient_receive_xrt_in_combination_with_bs_ab_no_0_yes_1",
              "h_o_plasma_cell_leukemia_no_0_yes_1",
              "eligible_for_corresponding_bs_ab_trial_on_first_dose_use_trial_elig_sheet_to_help_you_no_0_y_1",
              "step_up_initiated_inpatient_or_outpatient",
              "hemodialysis_pre_bs_ab_y_1_n_0",
              "icu_admission_during_first_cycle_n_0_y_1",
              "need_for_gcsf", "need_for_tpo_agonist",
              "ivig_n_0_y_1"
  ), 
  ~ case_when(
    . == 0                                              ~ "No",
    . == 1                                              ~ "Yes",
    TRUE                                                ~ as.character(.)
  )) %>% 
  mutate(prior_auto_sct_no_0_yes_1 = case_when(
    prior_auto_sct_no_0_yes_1 == "9"                    ~ "No",
    TRUE                                                ~ prior_auto_sct_no_0_yes_1
  )) |> 
  mutate(high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation = 
           as.numeric(high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation)) |> 
  mutate(high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation = case_when(
    high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation < 0.5        ~ "No",
    high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation > 0.5       ~ "Yes",
    TRUE       ~ as.character(high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation)
  )) |> 
  mutate(bs_ab_name_tec_1_tal_2_elra_3_linvo_4 = case_when(
    bs_ab_name_tec_1_tal_2_elra_3_linvo_4 == 1          ~ "Teclistamab",
    bs_ab_name_tec_1_tal_2_elra_3_linvo_4 == 2          ~ "Talquetamab",
    bs_ab_name_tec_1_tal_2_elra_3_linvo_4 == 3          ~ "Elra",
    bs_ab_name_tec_1_tal_2_elra_3_linvo_4 == 4          ~ "Linvo",
    TRUE                                                ~ NA_character_
  )) %>% 
  mutate(bs_ab_sud_inpatient_0_bs_ab_sup_outpatient_1 = case_when(
    bs_ab_sud_inpatient_0_bs_ab_sup_outpatient_1 == 0   ~ "Inpatient",
    bs_ab_sud_inpatient_0_bs_ab_sup_outpatient_1 == 1   ~ "Outpatient"
  )) |> 



  mutate(reason_no_date_of_first_bs_ab_full_dose = case_when(
    str_detect(date_of_first_bs_ab_full_dose, "([A-Za-z]+)")     ~ date_of_first_bs_ab_full_dose
  ), .after = date_of_first_bs_ab_full_dose) |> 
  # mutate(was_discontinued = case_when(
  #   date_of_disocntinuation_if_cotinues_enter_0 == 0     ~ "Continued",
  #   !is.na(date_of_disocntinuation_if_cotinues_enter_0)  ~ "Discontinued"
  # ), .after = ) %>%
  # Dates
  mutate(across(c(#"date_of_mm_diagnosis",
                  # "date_of_bs_ab_step_up_d1",
                  "date_of_first_bs_ab_full_dose",
                  # "date_of_max_ferritin",
                  # "date_of_max_crp",
                  # "date_of_onset_of_crs",
                  "date_of_max_crs",
                  # "date_of_onset_of_icans",
                  # "date_of_max_ican",
                  # "date_of_infection_1st",
                  # "date_of_infection_2nd",
                  # "date_of_infection_3rd",
                  # "date_of_infection_4th",
                  # "anc_nadir_date", "hgb_nadir_date",
                  # "plt_nadir_date", "date_of_ig_g_nadir",
                  # "date_of_first_ivig_dose_following_bs_ab_administration",
                  # "date_of_best_mrd_response_relative_to_bs_ab_start",
                  # "date_of_pd",
                  "date_of_discontinuation_if_continues_enter_0_bs_ab_stop_date"
                  # "date_of_death", "date_of_last_contact",
                  # "date_of_first_exposure_to_prior_bcma_agent",
                  # "date_of_last_exposure_to_prior_bcma_agent",
                  # "date_last_exposure",
                  # "while_on_bs_ab_date_of_first_documented_emd_response",
                  # "date_of_best_documented_emd_response",
                  # "date_of_last_imaging_before_data_cutoff_only_in_pts_who_are_still_responding"
                  ),
                ~ as.Date(as.numeric(.), 
                          # tryFormats = c("%m/%d/%y", "%m/%d/%Y"), 
                          origin = "1899-12-30")))
```

```{r}
data2 <- data1 %>% 
  # Age categories----
  mutate(age_cat = case_when(
    age_at_bs_ab_initiation < 70                                         ~ "< 70 years",
    age_at_bs_ab_initiation >= 70                                        ~ "≥ 70 years"
  ),
  age_cat = factor(age_cat, levels = c("< 70 years", "≥ 70 years")),
  .after = age_at_bs_ab_initiation
  ) %>%
  mutate(age_3cat = case_when(
    age_at_bs_ab_initiation < 65                                         ~ "< 65",
    age_at_bs_ab_initiation >= 65 &
      age_at_bs_ab_initiation < 75                                       ~ "65 to < 70",
    age_at_bs_ab_initiation >= 75                                        ~ "75 and above"
  ),
  age_3cat = factor(age_3cat, levels = c("< 65", "65 to < 70", "75 and above")),
  .after = age_cat
  ) %>%
  mutate(year_bsab = year(date_of_bs_ab_step_up_d1)) %>%
  # Sex categories----
  mutate(sex_0_male_1_female = case_when(
    sex_0_male_1_female == 0                  ~ "Male",
    sex_0_male_1_female == 1                  ~ "Female",
    TRUE                                      ~ as.character(sex_0_male_1_female)
  )) %>%
  mutate(male_sex = case_when(
    sex_0_male_1_female == "Male"                                    ~ 1,
    sex_0_male_1_female == "Female"                                  ~ 0
  ), .after = sex_0_male_1_female) %>%
  # Race eth
  rename_at(vars(contains("race")), ~ "race") %>%
  rename_at(vars(contains("hispanic")), ~ "ethnicity") %>%
  mutate(race = case_when(
    race == 0                                 ~ "White",
    race == 1                                 ~ "Black",
    race == 2                                 ~ "Asian American and Pacific Islander",
    race == 3                                 ~ "American indian",
    race == 4                                 ~ "Other",
    race == 5                                 ~ NA_character_,
    TRUE                                      ~ as.character(race)
  )) %>%
  mutate(ethnicity = case_when(
    ethnicity == 0                            ~ "Non-Hispanic",
    ethnicity == 1                            ~ "Hispanic",
    TRUE                                      ~ as.character(ethnicity)
  )) %>%
  mutate(raceeth = case_when(
    ethnicity == "Hispanic"                   ~ "Hispanic, any races",
    race == "White" &
      ethnicity == "Non-Hispanic"             ~ "White, Non-Hispanic",
    race == "Black" &
      ethnicity == "Non-Hispanic"             ~ "Black, Non-Hispanic",
    !is.na(race) &
      ethnicity == "Non-Hispanic"             ~ "Other, Non-Hispanic",
    TRUE                                      ~ NA_character_ # paste(race, ethnicity)
  ), raceeth = factor(raceeth, levels = c("White, Non-Hispanic",
                                          "Black, Non-Hispanic",
                                          "Hispanic, any races"))
  ) %>%
  # ECOG
  mutate_at(c("ecog_ps_at_bs_ab_initiation_0_5"), 
            ~ factor(.)
  ) %>%
  mutate(ecog_ps_at_bs_ab_initiation_0_5_cat = case_when(
    ecog_ps_at_bs_ab_initiation_0_5 == 0 |
      ecog_ps_at_bs_ab_initiation_0_5 == 1                                ~ "0-1",
    ecog_ps_at_bs_ab_initiation_0_5 %in% c(2:5)                           ~ "2-5"
  )) %>%
  mutate(weight_cat = case_when(
    weight_at_initiation_of_bs_ab_kg <= 70                                ~ "≤70",
    weight_at_initiation_of_bs_ab_kg > 70 &
      weight_at_initiation_of_bs_ab_kg <= 80                              ~ ">70 to 80",
    weight_at_initiation_of_bs_ab_kg > 80 &
      weight_at_initiation_of_bs_ab_kg <= 100                             ~ ">80 to 100",
    weight_at_initiation_of_bs_ab_kg > 100 &
      weight_at_initiation_of_bs_ab_kg <= 109                             ~ ">100 to 109",
    weight_at_initiation_of_bs_ab_kg > 109                                ~ ">109"
  ),
  weight_cat = factor(weight_cat, levels = c("≤70", ">70 to 80",
                                             ">80 to 100", ">100 to 109",
                                             ">109")),
  .after = weight_at_initiation_of_bs_ab_kg
  ) %>%
  # Myeloma
  rename(true_emd_prior_bsab_type = just_prior_to_bs_ab_initiation_is_there_true_emd_0_none_1_paraskeletal_only_2_true_emd_paraskeletal) |> 
  mutate(true_emd_prior_bsab_type = case_when(
    true_emd_prior_bsab_type == 0        ~ "None",
    true_emd_prior_bsab_type == 1        ~ "Paraskeletal only",
    true_emd_prior_bsab_type == 2        ~ "True EMD (+/-paraskeletal)",
    TRUE                                      ~ as.character(true_emd_prior_bsab_type)
  )) %>%
  mutate(true_emd_prior_bsab = case_when(
    true_emd_prior_bsab_type == "True EMD (+/-paraskeletal)"     ~ "Yes",
    true_emd_prior_bsab_type == "Paraskeletal only"              ~ "No",
    true_emd_prior_bsab_type == "None"                           ~ "No"
  )) %>%
  mutate(subtype = case_when(
    oligo_or_non_secretory_at_bs_ab_initiation_0_no_1_yes == "Yes"               ~ "Oligo/non-secretory",
    !is.na(myeloma_involved_heavy_chain_ig_g_ig_a_ig_m_ig_d_ig_e_or_blank) &
      !is.na(myeloma_involved_light_chain_kappa_lambda_biclonal_blank)           ~ "Intact immunoglobulin (Heavy + Light)",
    is.na(myeloma_involved_heavy_chain_ig_g_ig_a_ig_m_ig_d_ig_e_or_blank) &
     !is.na(myeloma_involved_light_chain_kappa_lambda_biclonal_blank)            ~ "Light chain only",
    TRUE           ~ paste(oligo_or_non_secretory_at_bs_ab_initiation_0_no_1_yes,
                           myeloma_involved_light_chain_kappa_lambda_biclonal_blank,
                           myeloma_involved_heavy_chain_ig_g_ig_a_ig_m_ig_d_ig_e_or_blank)
  ), subtype = relevel(as.factor(subtype), ref = "Oligo/non-secretory"
  )) %>%
  mutate(h_o_plasma_cell_leukemia_no_0_yes_1 = case_when(
    h_o_plasma_cell_leukemia_no_0_yes_1 == 2                        ~ "Yes",
    TRUE                                                            ~ h_o_plasma_cell_leukemia_no_0_yes_1
  )) |> 
  # Cytogenetics ----
  mutate(cytogenetics = case_when(
    deletion_17p_prior_to_bs_ab_0_no_1_yes == "Yes" |
      t_4_14_prior_to_bs_ab_0_no_1_yes == "Yes" |
      t_14_16_prior_to_bs_ab_0_no_1_yes == "Yes"                     ~ "High",
    deletion_17p_prior_to_bs_ab_0_no_1_yes == "No" &
      t_4_14_prior_to_bs_ab_0_no_1_yes == "No" &
      t_14_16_prior_to_bs_ab_0_no_1_yes == "No"                      ~ "Standard",
    TRUE                                                             ~ NA_character_
  ), .before = deletion_17p_prior_to_bs_ab_0_no_1_yes) %>%
  mutate(high_risk_cyto_newdef = case_when(
    deletion_17p_prior_to_bs_ab_0_no_1_yes == "Yes"                  ~ "High",
    t_4_14_prior_to_bs_ab_0_no_1_yes == "Yes" & 
      gain_amp1q21_prior_to_bs_ab_0_no_1_yes == "Yes"                              ~ "High",
    t_14_16_prior_to_bs_ab_0_no_1_yes == "Yes" & 
      gain_amp1q21_prior_to_bs_ab_0_no_1_yes == "Yes"                              ~ "High",
    t_4_14_prior_to_bs_ab_0_no_1_yes == "Yes" & 
      deletion_1p_0_no_1_yes == "Yes"                               ~ "High",
    t_14_16_prior_to_bs_ab_0_no_1_yes == "Yes" & 
      deletion_1p_0_no_1_yes == "Yes"                               ~ "High",
    gain_amp1q21_prior_to_bs_ab_0_no_1_yes == "Yes" & 
      deletion_1p_0_no_1_yes == "Yes"                               ~ "High",
    is.na(deletion_17p_prior_to_bs_ab_0_no_1_yes) | 
      is.na(t_4_14_prior_to_bs_ab_0_no_1_yes) | 
      is.na(t_14_16_prior_to_bs_ab_0_no_1_yes) | 
      is.na(gain_amp1q21_prior_to_bs_ab_0_no_1_yes) | 
      is.na(deletion_1p_0_no_1_yes)                                 ~ NA_character_, 
    TRUE                                                            ~ "Standard"
  )) %>%
  mutate(cytogenetics_doublehit = case_when(
    (deletion_17p_prior_to_bs_ab_0_no_1_yes == "Yes") +
    (deletion_1p_0_no_1_yes == "Yes") + 
      (gain_amp1q21_prior_to_bs_ab_0_no_1_yes == "Yes") +
      (t_4_14_prior_to_bs_ab_0_no_1_yes == "Yes") +
      (t_14_16_prior_to_bs_ab_0_no_1_yes == "Yes") >= 2             ~ "Yes",
    if_any(c(deletion_17p_prior_to_bs_ab_0_no_1_yes,
             deletion_1p_0_no_1_yes,
             gain_amp1q21_prior_to_bs_ab_0_no_1_yes,
             t_4_14_prior_to_bs_ab_0_no_1_yes,
             t_14_16_prior_to_bs_ab_0_no_1_yes), ~ is.na(.))        ~ NA_character_,
    TRUE                                                            ~ "No"
  ))# |> 
  # select(mrn, cytogenetics_doublehit, deletion_17p_prior_to_bs_ab_0_no_1_yes, t_4_14_prior_to_bs_ab_0_no_1_yes,
  #        t_14_16_prior_to_bs_ab_0_no_1_yes, deletion_1p_0_no_1_yes, gain_amp1q21_prior_to_bs_ab_0_no_1_yes)
```


```{r treatment}
data3 <- data2 %>% 
  mutate(number_of_prior_lines_of_therapy_before_bs_ab_cat = case_when(
    number_of_prior_lines_of_therapy_before_bs_ab <= 4                        ~ "≤ 4",
    number_of_prior_lines_of_therapy_before_bs_ab > 4                         ~ "> 4"
  ), .after = number_of_prior_lines_of_therapy_before_bs_ab) %>%  
  # Refractory status ----
  mutate_at(c("bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2",
              "carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2",
              "lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2",
              "pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2",
              "daratumumab_or_isatuximab_status_exposed_0_vs_refractory_1_vs_naive_2"
  ),
  ~ case_when(
    . == 0                                              ~ "Not refractory",
    . == 1                                              ~ "Refractory",
    . == 2                                              ~ "Not refractory",
    TRUE                                                ~ NA_character_
  )) %>%
  mutate(immuno = case_when(
    lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" |
      pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory"           ~ "Yes",
    lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 != "Refractory" |
      pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 != "Refractory"           ~ "No"
  ), .after = pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2) %>% 
  mutate(proteasome = case_when(
    bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" |
      carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory"            ~ "Yes",
    bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2 != "Refractory" |
      carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2 != "Refractory"            ~ "No"
  ), .after = immuno) %>%
  mutate(dara = case_when(
    daratumumab_or_isatuximab_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory"            ~ "Yes",
    is.na(daratumumab_or_isatuximab_status_exposed_0_vs_refractory_1_vs_naive_2)            ~ NA_character_,
    TRUE                                                           ~ "No"
  ), .after = daratumumab_or_isatuximab_status_exposed_0_vs_refractory_1_vs_naive_2) %>%
  mutate(doubleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes"                                              ~ "Yes",
    TRUE                                                           ~ "No"
  ), .after = proteasome) %>%
  mutate(tripleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes" &
      dara == "Yes"          ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(pentaref = case_when(
    bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" & 
      carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" &
      lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" & 
      pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" & 
      dara == "Yes"          ~ "Yes",
    TRUE                                                           ~ "No"
  )) |> 
  mutate(type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3 = case_when(
    type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3 == 1    ~ "ADC",
    type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3 == 2    ~ "CART",
    type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3 == 3    ~ "BsAb"
  )) |> 
  mutate(time_most_recent_bcma_to_initiation_days = 
           interval(
             start = date_of_last_exposure_to_prior_bcma_agent,
             end = date_of_bs_ab_step_up_d1)/
           duration(n=1, units = "days"),
         .after = date_of_last_exposure_to_prior_bcma_agent) %>%
  mutate(response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 = case_when(
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == "sCR" ~ "sCR",
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 1     ~ "CR",
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 2     ~ "VGPR",
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 3     ~ "PR",
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 4     ~ "SD",
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 5     ~ "PD",
  )) |> 
  mutate(time_last_gprc5d_to_initiation_days = 
           interval(
             start = date_of_last_gprc5d_exposure,
             end = date_of_bs_ab_step_up_d1)/
           duration(n=1, units = "days"),
         .after = date_of_last_gprc5d_exposure) %>%
  mutate(days_of_hospital_stay_days = case_when(
    inpatient_length_of_hospital_stay_days == 0                        ~ NA_real_,
    TRUE                                                            ~ inpatient_length_of_hospital_stay_days
  )) |> 
  mutate(days_of_icu_admission = case_when(
    days_of_icu_admission == 0                                      ~ NA_real_,
    TRUE                                                            ~ days_of_icu_admission
  ))
```

```{r baseline}
data4 <- data3 |> 
  mutate(baseline_b2m_prior_to_bs_ab_initiation = case_when(
    baseline_b2m_prior_to_bs_ab_initiation == -7.9                 ~ 15.5,
    TRUE                                                           ~ baseline_b2m_prior_to_bs_ab_initiation
  )) |> 
  # Any cytopenia (ANC<1500, WBC < 4, Hb <12 or Plt < 150)
  mutate(cytopenia_baseline = case_when(
    baseline_anc_k_u_l_ie_100_200_etc < 1.8 | 
      baseline_hgb < 11.4 | 
      baseline_pl_ts < 143                                             ~ "Yes",
    # if any is NA, we cannot truly code as No so NA
    is.na(baseline_anc_k_u_l_ie_100_200_etc) |
      is.na(baseline_hgb) |
      is.na(baseline_pl_ts)                                            ~ NA_character_,
    TRUE                                                              ~ "No"
  )) %>% 
  # Grade 3+ cytopenia (ANC<1000, Hb<8 or Plt<50) at day 30
  mutate(gr3_cytopenia_baseline = case_when(
    baseline_anc_k_u_l_ie_100_200_etc < 1 | 
      baseline_hgb < 8 | 
      baseline_pl_ts < 50                                             ~ "Yes",
    is.na(baseline_anc_k_u_l_ie_100_200_etc) |
      is.na(baseline_hgb) |
      is.na(baseline_pl_ts)                                            ~ NA_character_,
    TRUE                                                              ~ "No"
  ))

# Fix the "<" and ">" to take the min or max or each column including numbers next to the signs----
# Also replace "Suboptimal" by NA
vec_col <- c("baseline_ig_g_prior_to_bs_ab_initiation_mg_d_l"
             )
class(data4) <- "data.frame"

for (i in vec_col) {

  if (class(data4[, i]) == "character") {

    data4 <- data4 %>%
      mutate(wo_sign = as.numeric(str_remove(data4[, i], ">|<"))) %>%
      mutate(!!i := case_when(
        str_detect(data4[, i], ">")                 ~ max(wo_sign, na.rm = TRUE),
        str_detect(data4[, i], "<")                 ~ min(wo_sign, na.rm = TRUE),
        TRUE                                         ~ as.numeric(wo_sign)
      )) %>%
      select(-c(wo_sign))
  }
}
data4 <- data4 |> 
  mutate(hypogammaglobulinemia = case_when(
    baseline_ig_g_prior_to_bs_ab_initiation_mg_d_l < 400            ~ "<400",
    baseline_ig_g_prior_to_bs_ab_initiation_mg_d_l >= 400           ~ "≥400"
  ))

```


```{r toxicities}
data5 <- data4 %>% 
# CRS ----
  mutate(crs_any = ifelse(max_crs_grade_0_5 == 0, "No", "Yes"),
       crs_any2 = ifelse(crs_any == "No", 0, 1),
       crs_gradecat2 = case_when(
         max_crs_grade_0_5 == 0                        ~ "No CRS",
         max_crs_grade_0_5 == 1                        ~ "Grade 1",
         max_crs_grade_0_5 >= 2                        ~ "Grade 2+"),
       crs_gradecat2 = factor(crs_gradecat2, levels = c("No CRS", "Grade 1", "Grade 2+")),
       crs_gradecat3 = case_when(
         max_crs_grade_0_5 == 0                        ~ "No CRS",
         max_crs_grade_0_5 %in% c(1:2)                 ~ "Grade 1 or 2",
         max_crs_grade_0_5 >= 3                        ~ "Grade 3+"),
       crs_gradecat3 = factor(crs_gradecat3, levels = c("No CRS", "Grade 1 or 2", "Grade 3+"))
  ) %>%
  mutate(gr3_crs = case_when(
    max_crs_grade_0_5 %in% c(1:2)                      ~ "Grade <3",
    max_crs_grade_0_5 %in% c(3:5)                      ~ "Grade ≥3"
  )) %>%
  mutate(gr2_crs = case_when(
    max_crs_grade_0_5 %in% c(1)                        ~ "Grade <2",
    max_crs_grade_0_5 %in% c(2:5)                      ~ "Grade ≥2"
  )) %>%
  mutate(day_of_onset_crs_relative_to_initiation_days =
           interval(start = date_of_bs_ab_step_up_d1, end = date_of_onset_of_crs) /
           duration(n =1, unit = "days")
  ) %>%
  mutate(day_of_max_crs_relative_to_initiation =
           interval(start = date_of_bs_ab_step_up_d1, end = date_of_max_crs) /
           duration(n =1, unit = "days")
  ) |> 
  mutate(crs_14d = case_when(
    day_of_onset_crs_relative_to_initiation_days <= 14      ~ "CRS witin 14 days post initiation",
    day_of_onset_crs_relative_to_initiation_days > 14       ~ "No",
    crs_any == "No"                                    ~ "No"
  )) |> 
  mutate(crs_30d = case_when(
    day_of_onset_crs_relative_to_initiation_days <= 30      ~ "CRS witin 30 days post initiation",
    day_of_onset_crs_relative_to_initiation_days > 30       ~ "No",
    crs_any == "No"                                    ~ "No"
  )) |> 
  mutate(max_crs_grade_d14 = case_when(
    crs_14d == "CRS witin 14 days post initiation"     ~ max_crs_grade_0_5
  )) |> 
  mutate(max_crs_grade_d30 = case_when(
    crs_30d == "CRS witin 30 days post initiation"     ~ max_crs_grade_0_5
  )) |> 
  mutate(recurrent_crs_d14 = case_when(
    crs_14d == "CRS witin 14 days post initiation"     ~ recurrent_crs_n_0_y_1
  )) |> 
  mutate(recurrent_crs_d30 = case_when(
    crs_30d == "CRS witin 30 days post initiation"     ~ recurrent_crs_n_0_y_1
  )) |> 
  mutate(time_onset_crs_to_initiation_cat = case_when(
    day_of_onset_crs_relative_to_initiation_days == 1  ~ "1 day",
    day_of_onset_crs_relative_to_initiation_days == 2  ~ "2 day",
    day_of_onset_crs_relative_to_initiation_days > 2   ~ "more than 2 day"
  )) |> 
  # ICANS ----
  mutate(icans_any = ifelse(max_icans_grade == 0, "No", "Yes"),
       icans_any2 = ifelse(icans_any == "No", 0, 1),
       icans_gradecat2 = case_when(
         max_icans_grade == 0                      ~ "No ICANS",
         max_icans_grade == 1                      ~ "Grade 1",
         max_icans_grade >= 2                      ~ "Grade 2+"),
       icans_gradecat2 = factor(icans_gradecat2, levels = c("No ICANS", "Grade 1", "Grade 2+")),
       icans_gradecat3 = case_when(
         max_icans_grade == 0                      ~ "No ICANS",
         max_icans_grade %in% c(1:2)               ~ "Grade 1 or 2",
         max_icans_grade >= 3                      ~ "Grade 3+"),
       icans_gradecat3 = factor(icans_gradecat3, levels = c("No ICANS", "Grade 1 or 2", "Grade 3+")),
       gr3_icans = case_when(
         max_icans_grade %in% c(1:2)               ~ "Grade <3",
         max_icans_grade %in% c(3:5)               ~ "Grade ≥3"
       )) %>%
  mutate(gr2_icans = case_when(
    max_icans_grade %in% c(1)                      ~ "Grade <2",
    max_icans_grade %in% c(2:5)                    ~ "Grade ≥2"
  )) |> 
  mutate(day_of_onset_icans_relative_to_initiation_days =
           interval(start = date_of_bs_ab_step_up_d1, end = date_of_onset_of_icans) /
           duration(n =1, unit = "days")
  ) %>%
  mutate(day_of_max_icans_grade_relative_to_initiation =
           interval(start = date_of_bs_ab_step_up_d1, end = date_of_max_ican) /
           duration(n =1, unit = "days")
  ) |> 
  mutate(icans_14d = case_when(
    day_of_onset_icans_relative_to_initiation_days <= 14      ~ "ICANS witin 14 days post initiation",
    day_of_onset_icans_relative_to_initiation_days > 14       ~ "No",
    icans_any == "No"                                         ~ "No"
  )) |> 
  mutate(icans_30d = case_when(
    day_of_onset_icans_relative_to_initiation_days <= 30      ~ "ICANS witin 30 days post initiation",
    day_of_onset_icans_relative_to_initiation_days > 30       ~ "No",
    icans_any == "No"                                         ~ "No"
  )) |> 
  mutate(max_icans_grade_d14 = case_when(
    icans_14d == "ICANS witin 14 days post initiation"        ~ max_icans_grade
  )) |> 
  mutate(max_icans_grade_d30 = case_when(
    icans_30d == "ICANS witin 30 days post initiation"        ~ max_icans_grade
  )) |> 
  mutate(time_onset_icans_to_initiation_cat = case_when(
    day_of_onset_icans_relative_to_initiation_days == 1       ~ "1 day",
    day_of_onset_icans_relative_to_initiation_days == 2       ~ "2 day",
    day_of_onset_icans_relative_to_initiation_days > 2        ~ "more than 2 day"
  )) |> 
  mutate(concurent_crs_icans_d14 = case_when(
    crs_14d == "CRS witin 14 days post initiation" &
    icans_14d == "ICANS witin 14 days post initiation"        ~ "Yes",
    !is.na(icans_any) &
      !is.na(crs_any)                                         ~ "No"
  )) |> 
  
  mutate(treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain = str_replace(
    treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain,
    " and ", ", ")) %>%
  mutate(treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain = str_replace(
    treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain,
    "0", "No delay")) %>%
  mutate(treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain = str_replace(
    treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain,
    "1", "Infection")) %>%
  mutate(treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain = str_replace(
    treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain,
    "2", "Cytopenias")) %>%
  mutate(treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain = str_replace(
    treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain,
    "3", "CRS")) %>%
  mutate(treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain = str_replace(
    treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain,
    "4", "ICANS")) %>%
  mutate(treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain = str_replace(
    treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain,
    "5", "Other")) %>%
  mutate(treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain = 
           relevel(
             as.factor(treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain), 
             ref = "No delay")) |> 
  # mutate(treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain = case_when(
  # treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain == 1        ~ "Infection",
  # treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain == 2        ~ "Cytopenias",
  # treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain == 3        ~ "CRS",
  # treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain == 4        ~ "ICANS",
  # treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain == 5        ~ "Other",
  #   TRUE                                      ~ treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain
  # )) %>%
  mutate(ivig_n_0_y_1 = case_when(
    str_detect(ivig_n_0_y_1, "0")       ~ "No",
    str_detect(ivig_n_0_y_1, "1")       ~ "Yes"
  )) |> 
  mutate(ivig_given_regardless_of_ig_g_levels_0_or_ivig_given_in_response_to_low_ig_g_levels_1 = case_when(
    ivig_given_regardless_of_ig_g_levels_0_or_ivig_given_in_response_to_low_ig_g_levels_1 == 0      ~ "given_regardless_of_ig_g_levels",
    ivig_given_regardless_of_ig_g_levels_0_or_ivig_given_in_response_to_low_ig_g_levels_1 == 1      ~ "given_in_response_to_low_ig_g_levels"
  ))


```

```{r survival}
data6 <- data5 %>% 
  # pfs
  mutate(pfs_event = case_when(
    !is.na(date_of_pd) | !is.na(date_of_death)         ~ 1,
    TRUE                                               ~ 0
  ), .after = progression_yes_no) %>%
  mutate(pfs_date = coalesce(date_of_pd, date_of_death, date_of_last_contact),
         .after = death_yes_no) %>%
  mutate(pfs_time_from_initiation_months =
           interval(
             start = date_of_bs_ab_step_up_d1,
             end = pfs_date)/
           duration(n=1, units = "months"),
         .after = death_yes_no) %>%
  # os
  mutate(os_event = case_when(
    !is.na(date_of_death)                              ~ 1,
    TRUE                                               ~ 0
  ), .after = death_yes_no) %>%
  mutate(os_date = coalesce(date_of_death, date_of_last_contact),
         .after = death_yes_no) %>%
  mutate(os_time_from_initiation_months =
           interval(
             start = date_of_bs_ab_step_up_d1,
             end = os_date)/
           duration(n=1, units = "months"),
         .after = death_yes_no) %>%
  # TEC
  mutate(time_from_MM_to_bsab_months =
           interval(start = date_of_mm_diagnosis, end = date_of_bs_ab_step_up_d1) /
           duration(n =1, unit = "months")
  ) %>%

  # mutate(tec_end_date = coalesce(date_of_disocntinuation_if_cotinues_enter_0, pfs_date)
  # ) %>%
  # mutate(duration_of_tec_days =
  #          interval(start = date_of_bs_ab_step_up_d1, end = tec_end_date) /
  #          duration(n =1, unit = "days")
  # ) %>%
  # mutate(tec_event = case_when(
  #   discontinuation_yes_no == "Yes"           ~ 1,
  #   pfs_event == 1                            ~ 1,
  #   discontinuation_yes_no == "No" &
  #     pfs_event == 0                          ~ 0
  # )) %>%
  # mutate(duration_of_tec_days_cat = case_when(
  #   duration_of_tec_days <= median(duration_of_tec_days)               ~ "Low",
  #   duration_of_tec_days > median(duration_of_tec_days)                ~ "High"
  # )) %>%
  #   
#   
  mutate(reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain = case_when(
    reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain == 1        ~ "PD",
    reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain == 2        ~ "Toxicity",
    reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain == 3        ~ "Ongoing response",
    reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain == 4        ~ "Death",
    reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain == 5        ~ "Other",
    TRUE                                      ~ reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain
  )) %>%



  mutate(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain = str_replace(
    cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain,
    "1", "PD")) %>%
  mutate(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain = str_replace(
    cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain,
    "2", "Infection")) %>%
  mutate(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain = str_replace(
    cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain,
    "3", "CRS")) %>%
  mutate(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain = str_replace(
    cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain,
    "4", "ICANS")) %>%
  mutate(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain = str_replace(
    cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain,
    "5", "Other")) |> 
  
  # mutate(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain = case_when(
  #   cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain == 1        ~ "PD",
  #   cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain == 2        ~ "Infection",
  #   cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain == 3        ~ "CRS",
  #   cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain == 4        ~ "ICANS",
  #   cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain == 5        ~ "Others",
  #   TRUE                                      ~ as.character(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain)
  # ))
  mutate(any_invasive_second_primary_malignancy_exclude_non_melanoma_skin_cancer_dcis_etc_1_yes_2_no = case_when(
    any_invasive_second_primary_malignancy_exclude_non_melanoma_skin_cancer_dcis_etc_1_yes_2_no == 1 ~ "Yes",
    any_invasive_second_primary_malignancy_exclude_non_melanoma_skin_cancer_dcis_etc_1_yes_2_no == 2 ~ "No",
    any_invasive_second_primary_malignancy_exclude_non_melanoma_skin_cancer_dcis_etc_1_yes_2_no == 0 ~ "No",
    TRUE      ~ as.character(any_invasive_second_primary_malignancy_exclude_non_melanoma_skin_cancer_dcis_etc_1_yes_2_no)
  ))


  # mutate(time_from_tec_to_end_extraction_days =
  #          interval(start = date_of_bs_ab_step_up_d1, end = end_of_data_extraction) /
  #          duration(n =1, unit = "days")
  # )







# table(data6$progression_yes_no, data6$pfs_event)
# table(data6$death_yes_no, data6$os_event)
```


```{r response}
data7 <- data6 %>%   
  mutate(day30_response = case_when(
    (os_event == 1 | pfs_event == 1) &
      pfs_time_from_initiation_months < 1                               ~ "Died or progressed before day 30",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "EVAL")        ~ NA_character_,
    day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd == "NE"                    ~ NA_character_,
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "VGPR")        ~ "VGPR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "PR")          ~ "PR",
    # str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "UCR")	       ~ "UCR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "CR")          ~ "sCR or CR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "MR") |
      str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "SD")        ~ "SD",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "PD")          ~ "PD",
    is.na(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd)                     ~ NA_character_,
    TRUE                                                                ~ day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd
  ), .after = day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd) %>%
  mutate(day30_response_v2 = case_when(
    str_detect(day30_response, "Died")                               ~ "PD",
    is.na(day30_response)                                            ~ NA_character_,
    TRUE                                                             ~ day30_response
  ), .after = day30_response) %>%
  mutate(ORR_30days = case_when(
    str_detect(day30_response_v2, "CR|PR")                           ~ "PR or better",
    is.na(day30_response_v2)                                         ~ NA_character_,
    TRUE                                                             ~ "< PR"
  ), .after = day30_response_v2) %>%
  mutate(CRorbetter_30days = case_when(
    str_detect(day30_response_v2, "CR")	                             ~ "sCR or CR",
    is.na(day30_response_v2)                                         ~ NA_character_,
    TRUE                                                             ~ "< CR"
  ), .after = ORR_30days) %>%
  mutate(VGPRorbetter_30days = case_when(
    CRorbetter_30days == "sCR or CR"                        	       ~ "VGPR or better",
    day30_response_v2 == "VGPR"                        	             ~ "VGPR or better",
    is.na(day30_response_v2)                                         ~ NA_character_,
    TRUE                                                             ~ "< VGPR"
  ), .after = CRorbetter_30days) %>%
  # Day 90 response ----
  mutate(mon3_response = case_when(
    day30_response_v2 == "PD"                                         ~ "PD", #if was PD, is always PD
    (os_event == 1 | pfs_event == 1) &
      pfs_time_from_initiation_months < 3                             ~ "Died or progressed before 3 months",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "EVAL")      ~ NA_character_,
    day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd == "NE"                  ~ NA_character_,
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "VGPR")      ~ "VGPR",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "VPGR")      ~ "VGPR",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "PR")        ~ "PR",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "CR")	      ~ "sCR or CR",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "MR") |
      str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "SD")      ~ "SD",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "PD")        ~ "PD",
    is.na(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd)                   ~ NA_character_,
    TRUE           ~ day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd
  ), .after = day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd) %>%
  mutate(mon3_response_v2 = case_when(
    str_detect(mon3_response, "Died")                                 ~ "PD",
    is.na(mon3_response)                                              ~ NA_character_,
    TRUE                                                              ~ mon3_response
  ), .after = mon3_response) %>%
  mutate(ORR_mon3 = case_when(
    str_detect(mon3_response_v2, "CR|PR")                             ~ "PR or better",
    is.na(mon3_response_v2)                                           ~ NA_character_,
    TRUE                                                              ~ "< PR"
  ), .after = mon3_response_v2) %>%
  mutate(CRorbetter_mon3 = case_when(
    mon3_response_v2 == "sCR or CR"                        	          ~ "sCR or CR",
    is.na(mon3_response_v2)                                           ~ NA_character_,
    TRUE                                                              ~ "< CR"
  ), .after = ORR_mon3) %>%
  mutate(VGPRorbetter_mon3 = case_when(
    CRorbetter_mon3 == "sCR or CR"                        	          ~ "VGPR or better",
    mon3_response_v2 == "VGPR"                        	              ~ "VGPR or better",
    is.na(mon3_response_v2)                                           ~ NA_character_,
    TRUE                                                              ~ "< VGPR"
  ), .after = CRorbetter_mon3) %>%

    # Best response
  # mutate(ORR_as_best_response = case_when(
  #   ORR_30days == "PR or better" |
  #   ORR_mon3 == "PR or better" #|
  #   # ORR_mon6 == "ORR" |
  #   # ORR_mon9 == "ORR" |
  #   # ORR_mon12 == "ORR"
  #                                                                 ~ "PR or better",
  #   is.na(ORR_30days) &
  #     is.na(ORR_mon3) #&
  #     # is.na(ORR_mon6) &
  #     # is.na(ORR_mon9) &
  #     # is.na(ORR_mon12)
  #                                                                 ~ NA_character_,
  #    TRUE                                                         ~ "< PR"
  # ), .after = CRorbetter_mon3) %>%
  mutate(best_CRorbetter = case_when(
     CRorbetter_30days == "sCR or CR" |
       CRorbetter_mon3 == "sCR or CR" #|
       # CRorbetter_mon6 == "sCR or CR" |
       # CRorbetter_mon9 == "sCR or CR" |
       # CRorbetter_mon12 == "sCR or CR"
                                                                   ~ "sCR or CR",
     is.na(CRorbetter_30days) &
       is.na(CRorbetter_mon3) #&
       # is.na(CRorbetter_mon6) &
       # is.na(CRorbetter_mon9) &
       # is.na(CRorbetter_mon12)
                                                                   ~ NA_character_,
     TRUE                                                          ~ "< CR"
   ), .after = CRorbetter_mon3) %>%
  mutate(best_VGPRorbetter = case_when(
     VGPRorbetter_mon3 == "VGPR or better" |
       VGPRorbetter_30days == "VGPR or better"                     ~ "VGPR or better",
     is.na(VGPRorbetter_mon3) &
       is.na(VGPRorbetter_30days)                                  ~ NA_character_,
     TRUE                                                          ~ "< VGPR"
   ), .after = CRorbetter_mon3) %>%
  mutate(best_response = case_when(
    day30_response_v2 == "sCR or CR" |
      mon3_response_v2 == "sCR or CR" #|
      # mon6_response_v2 == "sCR or CR" |
      # mon9_response_v2 == "sCR or CR" |
      # mon12_response_v2 == "sCR or CR"
                                                                  ~ "sCR or CR",
    day30_response_v2 == "VGPR" |
      mon3_response_v2 == "VGPR" #|
      # mon6_response_v2 == "VGPR" |
      # mon9_response_v2 == "VGPR" |
      # mon12_response_v2 == "VGPR"
                                                                  ~ "VGPR",
    day30_response_v2 == "PR" |
      mon3_response_v2 == "PR" #|
      # mon6_response_v2 == "PR" |
      # mon9_response_v2 == "PR" |
      # mon12_response_v2 == "PR"
                                                                  ~ "PR",
    day30_response_v2 == "SD" |
      mon3_response_v2 == "SD" #|
      # mon6_response_v2 == "SD" |
      # mon9_response_v2 == "SD" |
      # mon12_response_v2 == "SD"
                                                                  ~ "SD",
    day30_response_v2 == "PD" |
      mon3_response_v2 == "PD" #|
      # mon6_response_v2 == "PD" |
      # mon9_response_v2 == "PD" |
      # mon12_response_v2 == "PD"
                                                                  ~ "PD",
    TRUE                                                          ~ NA_character_
  ), .after = best_CRorbetter) %>%
  mutate(best_ORRcollapsed = case_when(
    str_detect(best_response, "CR|PR")                            ~ "PR or better",
    str_detect(best_response, "SD|PD")                            ~ "< PR",
    TRUE                                                          ~ NA_character_
  ), .after = best_response) %>%
  mutate(best_response_s_cr_cr_vgpr_pr_mr_sd_pd = case_when(
    best_response_s_cr_cr_vgpr_pr_mr_sd_pd == "NE"                  ~ NA_character_,
    str_detect(best_response_s_cr_cr_vgpr_pr_mr_sd_pd, "VGPR")      ~ "VGPR",
    str_detect(best_response_s_cr_cr_vgpr_pr_mr_sd_pd, "VPGR")      ~ "VGPR",
    str_detect(best_response_s_cr_cr_vgpr_pr_mr_sd_pd, "PR")        ~ "PR",
    str_detect(best_response_s_cr_cr_vgpr_pr_mr_sd_pd, "CR")	      ~ "sCR or CR",
    str_detect(best_response_s_cr_cr_vgpr_pr_mr_sd_pd, "MR") |
      str_detect(best_response_s_cr_cr_vgpr_pr_mr_sd_pd, "SD")      ~ "SD",
    str_detect(best_response_s_cr_cr_vgpr_pr_mr_sd_pd, "PD")        ~ "PD",
    is.na(best_response_s_cr_cr_vgpr_pr_mr_sd_pd)                   ~ NA_character_,
    TRUE           ~ best_response_s_cr_cr_vgpr_pr_mr_sd_pd
  )) |> 
  # MRD----
  # mutate(across(c(contains("mrd_by_")),
  #           ~ case_when(
  #             . == "Positive"                                     ~ "Positive",
  #             . == "Negative"                                     ~ "Negative",
  #             TRUE                                                ~ NA_character_
  #           ))) %>%
  # mutate(MRD_day30 = coalesce(day_30_mrd_by_clono_seq_positive_vs_negative,
  #                              day_30_mrd_by_flow_positive_vs_negative
  # )) %>%
  # mutate(MRD_mon3 = coalesce(x3_month_mrd_by_clono_seq_positive_vs_negative,
  #                              x3_month_mrd_by_flow_positive_vs_negative
  # )) %>%
  # mutate(MRD_mon6 = coalesce(x6_month_mrd_by_clono_seq_positive_vs_negative,
  #                              x6_month_mrd_by_flow_positive_vs_negative
  # )) %>%
  # mutate(MRD_mon9 = coalesce(x9_month_mrd_by_clono_seq_positive_vs_negative,
  #                              x9_month_mrd_by_flow_positive_vs_negative
  # )) %>%
  # mutate(MRD_mon12 = coalesce(x12_month_mrd_by_clono_seq_positive_vs_negative,
  #                              x12_month_mrd_by_flow_positive_vs_negative
  # )) %>%
  # mutate(response_MRD_day30 = case_when(
  #   day30_response_v2 == "sCR or CR" &
  #     MRD_day30 == "Negative"                                     ~ "sCR or CR, MRD-",
  #   day30_response_v2 == "sCR or CR" &
  #     MRD_day30 == "Positive"                                     ~ "sCR or CR, MRD+",
  #   day30_response_v2 == "sCR or CR" &
  #     is.na(MRD_day30)                                            ~ "sCR or CR, MRD unknown",
  #   TRUE ~ day30_response_v2
  # )) %>%
  # mutate(response_MRD_mon3 = case_when(
  #   mon3_response_v2 == "sCR or CR" &
  #     MRD_mon3 == "Negative"                                      ~ "sCR or CR, MRD-",
  #   mon3_response_v2 == "sCR or CR" &
  #     MRD_mon3 == "Positive"                                      ~ "sCR or CR, MRD+",
  #   mon3_response_v2 == "sCR or CR" &
  #     is.na(MRD_mon3)                                             ~ "sCR or CR, MRD unknown",
  #   TRUE ~ mon3_response_v2
  # )) %>%
  # mutate(response_MRD_mon6 = case_when(
  #   mon6_response_v2 == "sCR or CR" &
  #     MRD_mon6 == "Negative"                                      ~ "sCR or CR, MRD-",
  #   mon6_response_v2 == "sCR or CR" &
  #     MRD_mon6 == "Positive"                                      ~ "sCR or CR, MRD+",
  #   mon6_response_v2 == "sCR or CR" &
  #     is.na(MRD_mon6)                                             ~ "sCR or CR, MRD unknown",
  #   TRUE ~ mon6_response_v2
  # )) %>%
  # mutate(response_MRD_mon9 = case_when(
  #   mon9_response_v2 == "sCR or CR" &
  #     MRD_mon9 == "Negative"                                      ~ "sCR or CR, MRD-",
  #   mon9_response_v2 == "sCR or CR" &
  #     MRD_mon9 == "Positive"                                      ~ "sCR or CR, MRD+",
  #   mon9_response_v2 == "sCR or CR" &
  #     is.na(MRD_mon9)                                             ~ "sCR or CR, MRD unknown",
  #   TRUE ~ mon9_response_v2
  # )) %>%
  # mutate(response_MRD_mon12 = case_when(
  #   mon12_response_v2 == "sCR or CR" &
  #     MRD_mon12 == "Negative"                                      ~ "sCR or CR, MRD-",
  #   mon12_response_v2 == "sCR or CR" &
  #     MRD_mon12 == "Positive"                                      ~ "sCR or CR, MRD+",
  #   mon12_response_v2 == "sCR or CR" &
  #     is.na(MRD_mon12)                                             ~ "sCR or CR, MRD unknown",
  #   TRUE ~ mon12_response_v2
  # )) %>%
  mutate(best_MRD_response = case_when(
    # prioritize clonoseq and then use flow
    best_response_mrd_clonoseq_positive_vs_negative == "Positive"  ~ "MRD+",
    best_response_mrd_clonoseq_positive_vs_negative == "Negative"  ~ "MRD-",
    best_response_mrd_flow_positive_vs_negative == "Positive"      ~ "MRD+",
    best_response_mrd_flow_positive_vs_negative == "Negative"      ~ "MRD-",
    !is.na(best_CRorbetter)                                        ~ "MRD unknown"
  )) %>%
  mutate(best_response_CR_MRD = case_when(
    best_CRorbetter == "sCR or CR"
    ~ paste0(best_CRorbetter, ", ", best_MRD_response),
    best_CRorbetter == "< CR"                                      ~ best_response
  )) |> 
  # mutate(best_response_MRD = case_when (
  #   response_MRD_day30 == "sCR or CR, MRD-" |
  #     response_MRD_mon3 == "sCR or CR, MRD-" |
  #     response_MRD_mon6 == "sCR or CR, MRD-" |
  #     response_MRD_mon9 == "sCR or CR, MRD-" |
  #     response_MRD_mon12 == "sCR or CR, MRD-"                      ~ "sCR or CR, MRD-",
  #    response_MRD_day30 == "sCR or CR, MRD+" |
  #     response_MRD_mon3 == "sCR or CR, MRD+" |
  #     response_MRD_mon6 == "sCR or CR, MRD+" |
  #     response_MRD_mon9 == "sCR or CR, MRD+" |
  #     response_MRD_mon12 == "sCR or CR, MRD+"                      ~ "sCR or CR, MRD+",
  #    response_MRD_day30 == "sCR or CR, MRD unknown" |
  #     response_MRD_mon3 == "sCR or CR, MRD unknown" |
  #     response_MRD_mon6 == "sCR or CR, MRD unknown" |
  #     response_MRD_mon9 == "sCR or CR, MRD unknown" |
  #     response_MRD_mon12 == "sCR or CR, MRD unknown"               ~ "sCR or CR, MRD unknown",
  #   TRUE ~ best_response
  # )) %>%
  # mutate(MRDneg_in_best_response = case_when(
  #   MRD_day30 ==  "Negative" |
  #     MRD_mon3 ==  "Negative" |
  #     MRD_mon6 ==  "Negative" |
  #     MRD_mon9 ==  "Negative" |
  #     MRD_mon12 ==  "Negative"                                    ~ "Negative",
  #   MRD_day30 ==  "Positive" |
  #   MRD_mon3 ==  "Positive" |
  #   MRD_mon6 ==  "Positive" |
  #   MRD_mon9 ==  "Positive" |
  #     MRD_mon12 ==  "Positive"                                    ~ "Positive",
#   TRUE                                                          ~ NA_character_
# )) %>%
  # mutate(bridging_response = case_when(
  #   response_to_bridging_chemotherapy == "MR" |
  #     response_to_bridging_chemotherapy == "SD/MR" |
  #     response_to_bridging_chemotherapy == "SD" |
  #     response_to_bridging_chemotherapy == "PD" |
  #     response_to_bridging_chemotherapy == "No"               ~ "SD/PD",
  #   response_to_bridging_chemotherapy == "CR" |
  #     response_to_bridging_chemotherapy == "PR" |
  #     response_to_bridging_chemotherapy == "VGPR"             ~ "PR or better",
  #   response_to_bridging_chemotherapy == "Not Evaluable" |
  #     response_to_bridging_chemotherapy == "ND" |
  #     response_to_bridging_chemotherapy == "Unknown"          ~ NA_character_,
  #   TRUE                                                      ~ NA_character_
  # ))
  mutate_at(c("best_response_to_treatment_number_1_after_post_bi_te_progression",
              "best_response_to_treatment_number_2_after_post_bi_te_progression"), ~ case_when(
    . == "NE"                  ~ NA_character_,
    str_detect(., "VGPR")      ~ "VGPR",
    str_detect(., "PR")        ~ "PR",
    str_detect(., "CR")	      ~ "sCR or CR",
    str_detect(., "MR") |
      str_detect(., "SD")      ~ "SD",
    str_detect(., "PD")        ~ "PD",
    is.na(.)                   ~ NA_character_,
    TRUE           ~ .
  ))
```

```{r cytopenia}
# cart2 <- cart2 #%>% 
  # # Any cytopenia (ANC<1500, WBC < 4, Hb <12 or Plt < 150)
  # mutate(cytopenia_baseline = case_when(
  #   baseline_anc_k_u_l_ie_100_200_etc < 1.8 | 
  #     baseline_hgb < 11.4 | 
  #     baseline_pl_ts < 143                                             ~ "Yes",
  #   # if any is NA, we cannot truly code as No so NA
  #   is.na(baseline_anc_k_u_l_ie_100_200_etc) |
  #     is.na(baseline_hgb) |
  #     is.na(baseline_pl_ts)                                            ~ NA_character_,
  #   TRUE                                                              ~ "No"
  # )) %>% 
  # # Grade 3+ cytopenia (ANC<1000, Hb<8 or Plt<50) at day 30
  # mutate(gr3_cytopenia_baseline = case_when(
  #   baseline_anc_k_u_l_ie_100_200_etc < 1 | 
  #     baseline_hgb < 8 | 
  #     baseline_pl_ts < 50                                             ~ "Yes",
  #   is.na(baseline_anc_k_u_l_ie_100_200_etc) |
  #     is.na(baseline_hgb) |
  #     is.na(baseline_pl_ts)                                            ~ NA_character_,
  #   TRUE                                                              ~ "No"
  # ))
```





```{r infection}







data8 <- data7 %>%
  # Fix - Remove data for a patient "The positive VRE surveillance screen consistent with colonization only"
  mutate(number_of_infections = case_when(
    infection_n_0_y_1 == "No" &
      number_of_infections > 0                          ~ 0,
    TRUE                                                ~ number_of_infections
  # ), number_of_infections = case_when(
  #   number_of_infections == 0                           ~ NA_real_,
  #   TRUE                                                ~ number_of_infections
  )) |> 
  mutate(infection_severity_1 = case_when(
    infection_n_0_y_1 == "No" &
      !is.na(infection_severity_1)                      ~ NA_character_,
    TRUE                                                ~ infection_severity_1
  )) |> 
  mutate(infection_type_1 = case_when(
    infection_n_0_y_1 == "No" &
      !is.na(infection_type_1)                          ~ NA_character_,
    TRUE                                                ~ infection_type_1
  )) |> 
  mutate(date_of_infection_1 = case_when(
    infection_n_0_y_1 == "No" &
      !is.na(date_of_infection_1)                       ~ NA_Date_,
    TRUE                                                ~ date_of_infection_1
  )) |> 
  mutate(pathogen = case_when(
    infection_n_0_y_1 == "No" &
      !is.na(pathogen)                                  ~ NA_character_,
    TRUE                                                ~ pathogen
  )) |> 
  # Missing 0 when no infection
  mutate(number_of_infections = case_when(
    !is.na(number_of_infections)                        ~ number_of_infections,
    is.na(number_of_infections) &
      infection_n_0_y_1 == "No"                         ~ 0,
  ))
  
  
  
  
  # Infection - fix data
  mutate(infection_severity_2 = case_when(
    date_of_infection_2 == date_of_bs_ab_step_up_d1     ~ infection_severity_3,
    TRUE                                                ~ infection_severity_2
  )) |> 
  mutate(infection_type_2 = case_when(
    date_of_infection_2 == date_of_bs_ab_step_up_d1     ~ infection_type_3,
    TRUE                                                ~ infection_type_2
  )) |> 
  mutate(date_of_infection_2 = case_when(
    date_of_infection_2 == date_of_bs_ab_step_up_d1     ~ date_of_infection_3,
    TRUE                                                ~ date_of_infection_2
  )) |> 
  mutate(infection_severity_1 = case_when(
    date_of_infection_1 == date_of_bs_ab_step_up_d1     ~ infection_severity_2,
    TRUE                                                ~ infection_severity_1
  ), infection_severity_1 = case_when(
    infection_severity_1 == "moderate"                  ~ "No",
    TRUE                                                ~ infection_severity_1
  )) |> 
  mutate(infection_type_1 = case_when(
    date_of_infection_1 == date_of_bs_ab_step_up_d1     ~ infection_type_2,
    TRUE                                                ~ infection_type_1
  )) |> 
  mutate(date_of_infection_1 = case_when(
    date_of_infection_1 == date_of_bs_ab_step_up_d1     ~ date_of_infection_2,
    TRUE                                                ~ date_of_infection_1
  )) |> 
  
  
  mutate(date_of_infection_1 = case_when(
    infection_n_0_y_1 == "No" &
      !is.na(date_of_infection_1)                       ~ NA_Date_,
    infection_n_0_y_1 == "Yes" &
      is.na(date_of_infection_1) &
      infection_type_1 == "Bacterial"                   ~ as.Date("2023-3-15"),
    infection_n_0_y_1 == "Yes" &
      is.na(date_of_infection_1) &
      infection_type_1 == "Fungal"                      ~ as.Date("2023-7-15"),
    infection_n_0_y_1 == "Yes" &
      is.na(date_of_infection_1) &
      infection_type_1 == "Viral"                       ~ as.Date("2026-2-12"),
    TRUE                                                ~ date_of_infection_1
  )) |> 
  mutate(time_from_bsab_therapy_to_1st_infection_days = 
           interval(
             start = date_of_bs_ab_step_up_d1, 
             end = date_of_infection_1)/
           duration(n=1, units = "days"),
     .after = date_of_infection_1) %>%
  mutate(time_from_bsab_therapy_to_1st_infection_months = 
           interval(
             start = date_of_bs_ab_step_up_d1, 
             end = date_of_infection_1)/
           duration(n=1, units = "months"),
     .after = date_of_infection_1) |> 
  # rename(any_infection = infection_n_0_y_1) %>%
  mutate(any_infection = case_when(
    infection_n_0_y_1 == 2                              ~ "Yes",
    TRUE                                                ~ infection_n_0_y_1
  )) |> 
  mutate(any_sevinfection = case_when(
    if_any(any_of(contains("infection_severity")), ~ . == "Yes")  ~ "Yes",
    if_any(any_of(contains("infection_severity")), ~ !is.na(.))   ~ "No"
  )) #|> 
  # select(mrn, any_infection, contains("infection"))
  
  
  
  
  # mutate(time_from_bsab_therapy_to_1st_infection_days_d30 = case_when(
  #   time_from_bsab_therapy_to_1st_infection_days <= 30  ~ time_from_bsab_therapy_to_1st_infection_days
  # )) 


a <- data8 |> select(mrn, patient_identifier,
                     date_of_bs_ab_step_up_d1, pathogen, number_of_infections, infection_n_0_y_1,
         starts_with("infection_type_"), starts_with("date_of_infection_"), starts_with("infection_severity_"))



bsab_inf <-
  data8 |> 
  select(mrn, date_of_bs_ab_step_up_d1, pathogen, number_of_infections, infection_n_0_y_1,
         starts_with("infection_type_"), starts_with("date_of_infection_"), starts_with("infection_severity_")) |> 
  mutate(pathogen = str_replace(pathogen, "^,", "empty,")) |> 
  mutate(pathogen = str_replace_na(pathogen, "empty")) |> 
  mutate(pathogen_count = sapply(strsplit(pathogen, ","), length), .after = pathogen) %>% 
  separate_wider_delim(cols = pathogen, delim = ", ",
                       names = c(paste("pathogen", 1:max(.$pathogen_count), sep = "_")), 
                       too_few = "align_start", too_many = "merge", 
                       cols_remove = TRUE) |> 
  pivot_longer(cols = -c(mrn, date_of_bs_ab_step_up_d1, number_of_infections, infection_n_0_y_1), 
               names_pattern = "(date_of_infection|infection_type|infection_severity|pathogen)(_1|_2|_3|_4).*",
               names_to = c(".value", "sequence"), 
               values_drop_na = TRUE) |> 
  # 4 patients (5 dates) are identical as date of bsab - exclude
  mutate(infection_severity = case_when(
    date_of_infection == date_of_bs_ab_step_up_d1       ~ "REMOVE",
    TRUE                                                ~ infection_severity
  )) |> 
  mutate(infection_type = case_when(
    date_of_infection == date_of_bs_ab_step_up_d1       ~ NA_character_,
    TRUE                                                ~ infection_type
  )) |> 
  mutate(pathogen = case_when(
    date_of_infection == date_of_bs_ab_step_up_d1       ~ NA_character_,
    TRUE                                                ~ pathogen
  )) |> 
  mutate(date_of_infection = case_when(
    date_of_infection == date_of_bs_ab_step_up_d1       ~ NA_Date_,
    TRUE                                                ~ date_of_infection
  )) |>
  select(-sequence) |> 
  arrange(mrn, date_of_infection) |> 
  # mutate(any_infection = case_when(
  #   number_of_infections == 0                           ~ "No"
  # ))
  group_by(mrn) |> 
  mutate(number_of_infections = row_number()) |> 
  ungroup() |> 
  filter(!(number_of_infections > 1 & infection_severity == "REMOVE") |
           number_of_infections == 0) |> 
    mutate(number_of_infections = case_when(
      infection_severity == "REMOVE"            ~ 0,
      TRUE                                      ~ number_of_infections
    )) |> 
    mutate(infection_severity = na_if(infection_severity, "REMOVE"))



# calculate time for each infection
    mutate(time_from_bsab_therapy_to_infection_days = 
             interval(
             start = date_of_bs_ab_step_up_d1, 
             end = date_of_infection) /
           duration(n=1, units = "days")) |> 
  arrange(mrn, time_from_bsab_therapy_to_infection_days) |> 
  # pick infection and severity within 30 days
  mutate(any_infection_d30 = case_when(
    time_from_bsab_therapy_to_infection_days <= 30 &
      any_infection == "Yes"                              ~ "Yes"
  )) |> 
  mutate(any_sevinfection_d30 = case_when(
    time_from_bsab_therapy_to_infection_days <= 30 &
      infection_severity == "Yes"                         ~ "Yes"
  )) |> 
  # fill Yes per patient
  group_by(mrn) |> 
  fill(any_infection_d30, any_sevinfection_d30, .direction = "updown") |> 
  ungroup() |> 
  # Add No
  mutate(any_infection_d30 = case_when(
      any_infection_d30 == "Yes"                            ~ "Yes",
    time_from_bsab_therapy_to_infection_days > 30     ~ "No",
    any_infection == "No"                               ~ "No"
  )) |> 
  mutate(any_sevinfection_d30 = case_when(
      any_sevinfection_d30 == "Yes"                         ~ "Yes",
    time_from_bsab_therapy_to_infection_days > 30      ~ "No",
    infection_severity == "No"                            ~ "No"
  )) |> 
  # pick type of infection within 30 days
    mutate(infection_type_d30 = case_when(
      time_from_bsab_therapy_to_infection_days <= 30   ~ infection_type
    )) |> 
  select(mrn, any_infection_d30, any_sevinfection_d30, infection_type_d30) |> 
  arrange(mrn, infection_type_d30) |> 
  group_by(mrn, any_infection_d30, any_sevinfection_d30) |> 
  summarise_at(vars(infection_type_d30), str_c, collapse = "; ") |> 
  ungroup()

bsab_data1 <- bsab_data |> 
  left_join(bsab_inf, by = "mrn") |> 
  select(mrn, any_infection, any_sevinfection, any_infection_d30, any_sevinfection_d30, infection_type_d30)
  mutate(any_infection_d30 = coalesce(any_infection_d30, any_infection)) |> 
  mutate(any_sevinfection_d30 = case_when(
      any_sevinfection_d30 == "Yes"                         ~ "Yes",
    time_from_bsab_therapy_to_infection_days > 30      ~ "No",
    infection_severity == "No"                            ~ "No"
  )) |> 



```

```{r Labeling}
var_label(bsab_data) <- list(age_at_bs_ab_initiation = "Patient age", age_cat = "Patient age - Categories", 
                             age_3cat = "Patient age - Categories", 
                             bs_ab_name_tec_1_tal_2_elra_3_linvo_4 = "Therapy name",
                             bs_ab_served_only_as_pre_car_t_bridging_0_no_1_yes = "Served as pre-CART bridging",
                             
                             male_sex = "Male Sex", sex_0_male_1_female = "Sex",
                             race = "Race",
                             ethnicity = "Ethnicity",
                             raceeth = "Race and ethnicity",
                             # # extramedullary_disease_yes_no = "Extramedullary disease",
                             # # circulating_plasma_cell = "UPDATED Circulating Plasma Cells",
                             high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation =
                               "High marrow burden (≥50%)",
                             ecog_ps_at_bs_ab_initiation_0_5 = "ECOG PS at therapy initiation",
                             ecog_ps_at_bs_ab_initiation_0_5_cat = "ECOG PS at therapy initiation (categorical)",
                             time_from_MM_to_bsab_months = "Time from MM diagnosis to BsAb (months)",
                             # duration_of_tec_days = "Duration of BsAb",
                             # # duration_of_tec_days_cat = "Duration of BsAb (cat)",
                             # time_from_tec_to_end_extraction_days = 
                             #   "Follow-up period from BsAb initiation to end of data extraction (days)",
                             year_bsab = "Year of BsAb",
                             # r_iss_at_car_t_initiation = "R-ISS at cart initiation",
                             subtype = "Subtype",
                             oligo_or_non_secretory_at_bs_ab_initiation_0_no_1_yes = "Oligo or non secretory at initiation",
                             myeloma_involved_heavy_chain_ig_g_ig_a_ig_m_ig_d_ig_e_or_blank = "Myeloma involved heavy chain",
                             myeloma_involved_light_chain_kappa_lambda_biclonal_blank = "Myeloma involved light chain",
                             prior_cart_0_no_1_yes = "Received prior CART",
                             # amyloidosis_if_yes_fill_out_amyloid_sheet_as_well_please_once_youre_done_with_this_one_0_no_1_yes =
                             #   "Amyloidosis",
                             h_o_plasma_cell_leukemia_no_0_yes_1 = "History of plasma cell leukemia",
                             # active_cns_mm_if_yes_fill_out_cns_sheet_as_well_once_done_with_this_one_0_no_1_yes = 
                             #   "Active CNS",
                             # pcl_5_percent_cp_cs_at_any_point_from_dx_through_last_pre_bs_ab_lo_t_0_no_1_secondary_pcl_not_at_dx_2_primary_pcl_at_dx = 
                             #   "PCL (?5% CPCs) at any point from Dx through last pre-BsAb LoT?",
                             # active_pcl_5_percent_cp_cs_within_30_days_prior_or_after_bs_ab_initiation_0_no_1_yes = 
                             #   "Active PCL (?5% CPCs) within 30 days prior or after BsAb initiation?",
                             # is_percent_cp_cs_checked_within_30_days_before_bs_ab_initiation = 
                             #   "is % CPCs checked within 30 days before BsAb initiation?",
                             # percent_cp_cs_if_pb_checked_within_30_days_before_bs_ab_initiation = 
                             #   "% CPCs if PB checked within 30 days before BsAb initiation",
                             prophylactic_tocilizumab_n_0_y_1 = "Prophylactic Tocilizumab",
                             # 
                             cytogenetics = "High risk cytogenetics (not include gain 1q)",
                             high_risk_cyto_newdef = "High risk cytogenetics (New definition)",
                             cytogenetics_doublehit = "High risk cytogenetics (Double hit)",
                             deletion_17p_prior_to_bs_ab_0_no_1_yes = "Deletion 17p at initiation",
                             t_4_14_prior_to_bs_ab_0_no_1_yes = "t(4:14) at initiation",
                             t_14_16_prior_to_bs_ab_0_no_1_yes = "t(4:16) at initiation",
                             gain_amp1q21_prior_to_bs_ab_0_no_1_yes = "Gain/amp 1q21",
                             amp_1_q_only_0_no_1_yes = "Amp 1q only",
                             deletion_1p_0_no_1_yes = "Deletion 1p",
                             number_of_prior_lines_of_therapy_before_bs_ab = "Number of prior lines of therapy",
                             number_of_prior_lines_of_therapy_before_bs_ab_cat = "Number of prior lines of therapy (cat)",
                             # bridging_therapy_yes_no = "Bridging Therapy",
                             prior_auto_sct_no_0_yes_1 = "Prior autoSCT",
                             # prior_allo_sct_within_6_months_before_apheresis = "Prior alloSCT",
                             prior_bcma_directed_therapy_no_0_y_1 = "Prior BCMA-directed therapy",
                             type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3 = "Type most recent BCMA agent",
                             # most_recent_bcma_agent_name = "Name most recent BCMA agent",
                             response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 =
                               "Response most recent BCMA agent",
                             need_for_gcsf = "Granulocyte colony stimulating factor (G-CSF)",
                             need_for_tpo_agonist = "Thrombopoietin (TPO) agonist",
                             ivig_n_0_y_1 = "Intravenous immunoglobulin (IVIG)",
                             # ivig_cat = "IVIG (categories)",
                             # # cd34_stem_cell_boost_yes_1_no_0 = "CD34 stem cell boost",
                             # # day_of_neutrophil_recovery = "Day of neutrophil recovery",
                             # # transfusion_postCART = "Transfusion post-CAR T",
                             steroid_use_as_tx_n_0_y_1 = "Steroid Use", 
                             tocilizumab_as_tx_n_0_y_1 = "Tocilizumab Use", 
                             anakinra_n_0_y_1 = "Anakinra Use",
                             proteasome = "Refractory to Proteasome Inhibitors",
                             lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 = "Refractory to Lenalidomide",
                             bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2 = "Refractory to Bortezomib",
                             carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2 = "Refractory to Carfilzomib",
                             pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 = "Refractory to Pomalidomide",
                             dara = "Refractory to Daratumumab or Isatuximab",
                             immuno = "Refractory to Immunomodulators", doubleref = "Double refractory",
                             triple_class_refractory_i_mi_d_pi_anti_cd38_no_0_y_1= "Triple refractory",
                             penta_refractory_2_p_is_2_i_mi_ds_anti_cd38_no_0_y_1= "Penta refractory",
                             pentaref = "Penta refractory",
                             
                             baseline_anc_k_u_l_ie_100_200_etc = "Baseline ANC (k/ul, ie. 100, 200, etc)",
                             baseline_hgb = "Baseline HGB",
                             baseline_pl_ts = "baseline PLTs",
                             baseline_alc_k_u_l_ie_100_200_etc = "Baseline ALC (k/ul, ie. 100, 200, etc)",
                             baseline_cr_cl_m_l_min = "Baseline CrCl (ml/min)",
                             hemodialysis_pre_bs_ab_y_1_n_0 = "Hemodialysis pre-BsAb",
                             # hemodialysis_post_bs_ab_y_1_n_0 = "Hemodialysis post-BsAb",
                             baseline_b2m_prior_to_bs_ab_initiation = "Baseline B2M prior to therapy",
                             baseline_ldh_prior_to_bs_ab_initiation_u_l = "Baseline LDH prior to therapy (u/l)",
                             baseline_albumin_prior_to_bs_ab_initiation_g_d_l = "Baseline albumin prior to therapy (g/dl)",
                             baseline_ferritin_prior_to_bs_ab_initiation_ng_m_l = "Baseline ferritin prior to therapy (ng/ml)",
                             max_ferritin = "Max ferritin",
                             baseline_crp_prior_to_bs_ab_initiation_mg_l = "Baseline CRP prior to therapy (mg/l)",
                             max_crp = "Max CRP",
                             baseline_ig_g_prior_to_bs_ab_initiation_mg_d_l = "Baseline Igg prior to therapy (mg/dl)",
                             hypogammaglobulinemia = "Hypogammaglobulinemia",
                             cytopenia_baseline = "Any Cytopenia (baseline)",
                             gr3_cytopenia_baseline = "Any Grade3+ Cytopenia (baseline)",
                             # alc_day_8 = "ALC day8",
                             # alc_day_15 = "ALC day15",
                             # alc_day_22 = "ALC day22",
                             # alc_c2d1 = "ALC C2D1",
                             # c2d1_ig_g_level_if_checked_mg_d_l = "C2D1 Igg (mg/dl)",
                             # anc_nadir_value_during_first_6_cycles_k_u_l_ie_100_200_etc = "ANC during first 6 cycles (nadir)",
                             # hgb_nadir_value_during_first_6_cycles = "HGB during first 6 cycles (nadir)",
                             # plt_nadir_value_during_first_6_cycles = "PLT during first 6 cycles (nadir)",
                             # ig_g_nadir_during_first_6_cycles_mg_d_l = "Igg during first 6 cycles (nadir)",
                             # cr_cl_prior_to_step_up_dose_number_1_m_l_min = "CrCl prior to step up dose 1 (ml/min)",
                             # cr_cl_at_d30 = "CrCl day 30",
                             # cr_cl_at_d90 = "CrCl day 90",
                             # number_of_prior_bcma_directed_agents = "Number of prior BCMA",
                             prior_adc_no_0_yes_1 = "Prior ADC",
                             if_prior_adc_which_one_s = "Prior ADC name",
                             prior_cart_0_no_1_yes = "Prior CART",
                             if_prior_cart_which_one_s = "Prior CART name",
                             # prior_bs_ab_yes_no = "Prior BsAb",
                             # prior_bs_ab_name = "Prior BsAb name",
                             prior_gprc5d_yes_no = "Prior GPRC5D",
                             # talquetamab_toxicities_oral_toxicities_e_g_dysgeusia_if_so_describe =
                             #   "Talquetamab toxicities",
                             true_emd_prior_bsab =
                               "True EMD prior to BsAb initiation",
                             # total_number_true_emd_plasmacytomas_if_1_2_sites_write_1_or_2_if_2_plasmacytomas_just_write_3 =
                             #   "Total number true EMD",
                             # locations_of_true_emd_be_specific = "Locations of true EMD",
                             # if_yes_what_location_0_same_site_1_new_site_2_both = "If yes, what location",
                             # concurrent_biochemical_relpase_yes_no = "Concurrent biochemical relpase",
                             # concurrent_pmd_relapse_yes_no = "concurrent PMD relapse",
                             # 
                             # total_number_paraskelatal_plasmacytomas = "Total number paraskelatal plasmacytomas",
                             # true_emd_relapse_yes_no = "True EMD relapse",
                             # best_documented_emd_response = "Best documented EMD response",
                             # xrt_2_weeks_before_and_after_3_months_of_bs_ab_starting_yes_no_response =
                             #   "XRT 2 weeks before and after  3 months of BsAb",
                             max_crs_grade_0_5 = "CRS Grade (0-5)", crs_any = "Any CRS", 
                             crs_gradecat2 = "CRS Grade", crs_gradecat3 = "CRS Grade", 
                             gr2_crs = "Grade2 CRS",
                             gr3_crs = "Grade3 CRS",
                             recurrent_crs_n_0_y_1 = "Recurrent CRS",
                             max_icans_grade = "ICANS Grade (0-5)", icans_any = "Any ICANS", 
                             icans_gradecat2 = "ICANS Grade", icans_gradecat3 = "ICANS Grade", 
                             gr2_icans = "Grade 2 ICANS",
                             gr3_icans = "Grade 3 ICANS",
                             day_of_onset_crs_relative_to_initiation_days = "Day of onset of CRS relative to initiation",
                             day_of_max_crs_relative_to_initiation = "Day of Max CRS (relative to initiation)",
                             duration_of_crs_days = "Duration of CRS (days)",
                             day_of_onset_icans_relative_to_initiation_days = "Day of onset of ICANS relative to initiation",
                             day_of_max_icans_grade_relative_to_initiation = "Day of Max ICANS (relative to initiation)",
                             duration_of_icans_days = "Duration of ICANS (days)",
                             # delayed_neuro = "Delayed Neurotoxicity",
                             # parkinsonian_neurotoxicity_yes_no = "Parkinsonian Neurotoxicity",
                             # other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = 
                             #   "Other/Delayed Non-Parkinsonian Neurologic Toxicity",
                             # delayed_neuro_type = "Delayed Neurotoxicity Type",
                             # hlh = "HLH", hlh_hlh_like_toxicities = "HLH/HLH-Like Toxicities?",
                             # overall_hlh = "Combined HLHs",
                             any_infection = "Any infection",
                             any_sevinfection = "Any severe infection",
                             time_from_bsab_therapy_to_1st_infection_days = "Time from BsAb to 1st infection (days)",
                             number_of_infections = "Total number of infections (if any)",
                             infection_type_1 = "Infection type (1st)",
                             infection_severity_1 = "Infection severity (1st)",
                             infection_type_2 = "Infection type (2nd)",
                             infection_severity_2 = "Infection severity (2nd)",
                             infection_type_3 = "Infection type (3rd)",
                             infection_severity_3 = "Infection severity (3rd)",
                             infection_type_4 = "Infection type (4th)",
                             infection_severity_4 = "Infection severity (4th)",
                             
                             treatment_delays_during_first_cycle_no_delays_0_infection_1_cytopenias_2_crs_3_icans_4_other_5_explain =
                               "Cause for treatment delays during first cycle",
                             icu_admission_during_first_cycle_n_0_y_1 = "ICU admission during first cycle",
                             days_of_icu_admission = "Days of ICU admission (if any)",
                             days_of_hospital_stay_days = "Days of inpatient hospital stay (if any)",
                             bs_ab_sud_inpatient_0_bs_ab_sup_outpatient_1 = "In/Out patient",
                             inpatient_length_of_hospital_stay_days =
                               "Inpatient length of hospital stay total (days, include 0)",
                             # tbv = "TBV", whole_blood_processed_m_l = "Whole blood processed (mL)",
                             # final_collection_volume_m_l = "Final collection volume (mL)", 
                             # tbv_processed = "TBV processed", 
                             # access_type = "Access type", total_bags = "Total bags",
                             # run_time_min = "Run time (min)",
                             # total_dose_volume_m_l = "Total dose volume (mL)", 
                             # cell_dose_million_cells = "Total cell dose (million cells)",
                             day30_response_v2 = "Day 30 Response (Collapsed)",
                             ORR_30days = "Day 30 ORR",
                             VGPRorbetter_30days = "Day 30 VGPR or better",
                             CRorbetter_30days = "Day 30 CR or better",
                             mon3_response_v2 = "Day 90 Response (Collapsed)",
                             ORR_mon3 = "Day 90 ORR",
                             VGPRorbetter_mon3 = "Day 90 VGPR or better",
                             CRorbetter_mon3 = "Day 90 CR or better",
                             # 
                             best_response = "Best Response",
                             best_VGPRorbetter = "Best VGPR or better",
                             best_CRorbetter = "Best CR or better",
                             best_ORRcollapsed = "Best ORR",
                             best_MRD_response = "Best MRD response",
                             best_response_CR_MRD = "Best MRD - CR or better",
                             # best_response_s_cr_cr_vgpr_pr_mr_sd_pd = "Raw best response",
                             # best_response_mrd_flow_positive_vs_negative = "Raw best MRD response (flow)",
                             # best_response_mrd_clonoseq_positive_vs_negative = "Raw best MRD response (clonoseq)",
                             progression_yes_no = "Progression (Death events excluded)",
                             pfs_event = "PFS events",
                             pfs_time_from_initiation_months = "PFS time (months)",
                             # pfs_with_1st_line_mm_diagnosis_18_months_0_no_1_yes = "Functional high-risk",
                             death_yes_no = "Death",
                             os_event = "OS events",
                             os_time_from_initiation_months = "Follow-up time from initiation (months)",
                             cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain =
                               "Cause of death",
                             
                             # discontinuation_yes_no = "Discontinuation",
                             
                             eligible_for_corresponding_bs_ab_trial_on_first_dose_use_trial_elig_sheet_to_help_you_no_0_y_1 =
                               "Eligible for corresponding BsAb trial on first dose"#,
) 

```
<br>

<!-- This analysis restricted to patient who received IVIG -->
<!-- ```{r} -->
<!-- bsab_data <- bsab_data %>%  -->
<!--   filter(ivig_cat != "No IVIG") -->
<!-- ``` -->


# Tables
## Table Demographic
```{r Table 1}
bsab_data %>% 
  select(age_at_bs_ab_initiation, age_cat, age_3cat,
         # male_sex, 
         sex_0_male_1_female,
         race,
         ethnicity,
         raceeth,
         weight_cat,
         weight_at_initiation_of_bs_ab_kg,
         prophylactic_tocilizumab_n_0_y_1
         ) %>%
  tbl_summary(by = prophylactic_tocilizumab_n_0_y_1,
              type = list(c(age_at_bs_ab_initiation, weight_at_initiation_of_bs_ab_kg) ~ "continuous2",
                          c(all_dichotomous()#, -male_sex
                            ) ~ "categorical"),
              statistic = list(c(all_continuous2()) ~ c(
                "{mean} ({sd})",
                "{median} ({p25}, {p75})",
                "{min}, {max}")), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_spanning_header(all_stat_cols() ~ "Prophylactic Tocilizumab") %>% 
  remove_footnote_header(columns = everything()) %>% as_gt()
```

## Table Clinical
```{r Table Clinical}
bsab_data %>% 
  select(ecog_ps_at_bs_ab_initiation_0_5,
         ecog_ps_at_bs_ab_initiation_0_5_cat,
         cytogenetics, high_risk_cyto_newdef, cytogenetics_doublehit,
         deletion_17p_prior_to_bs_ab_0_no_1_yes,
         t_4_14_prior_to_bs_ab_0_no_1_yes, t_14_16_prior_to_bs_ab_0_no_1_yes, gain_amp1q21_prior_to_bs_ab_0_no_1_yes,
         amp_1_q_only_0_no_1_yes, deletion_1p_0_no_1_yes,
         eligible_for_corresponding_bs_ab_trial_on_first_dose_use_trial_elig_sheet_to_help_you_no_0_y_1,
         h_o_plasma_cell_leukemia_no_0_yes_1,
         true_emd_prior_bsab, true_emd_prior_bsab_type,
         
         baseline_ferritin_prior_to_bs_ab_initiation_ng_m_l,
         baseline_b2m_prior_to_bs_ab_initiation, 
         baseline_cr_cl_m_l_min, 
         baseline_ldh_prior_to_bs_ab_initiation_u_l, 
         baseline_hgb, 
         baseline_pl_ts, 
         baseline_anc_k_u_l_ie_100_200_etc,
         baseline_alc_k_u_l_ie_100_200_etc,
         baseline_ig_g_prior_to_bs_ab_initiation_mg_d_l,
         hypogammaglobulinemia,
         
         time_from_MM_to_bsab_months,
         high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation,
         prophylactic_tocilizumab_n_0_y_1
         ) %>%
  tbl_summary(by = prophylactic_tocilizumab_n_0_y_1,
              type = list(#c(days_of_icu_admission) ~ "continuous",
                          c(all_continuous()) ~ "continuous2",
                          c(all_dichotomous()#, -male_sex
                            ) ~ "categorical"),
              statistic = list(c(all_continuous2()) ~ c(
                "{mean} ({sd})",
                "{median} ({p25}, {p75})",
                "{min}, {max}")), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_spanning_header(all_stat_cols() ~ "Prophylactic Tocilizumab") %>% 
  remove_footnote_header(columns = everything()) %>% as_gt()
```

## Table Treatment history
```{r Table Treatment history}
bsab_data %>% 
  select(bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2, carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2, 
         proteasome, 
         lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2, pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2, 
         immuno, 
         dara, 
         doubleref, 
         triple_class_refractory_i_mi_d_pi_anti_cd38_no_0_y_1, 
         penta_refractory_2_p_is_2_i_mi_ds_anti_cd38_no_0_y_1,
         prior_cart_0_no_1_yes, if_prior_cart_which_one_s,
         prior_adc_no_0_yes_1, if_prior_adc_which_one_s, 
         prior_bcma_directed_therapy_no_0_y_1, 
         type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3, most_recent_bcma_agent_name, 
         response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6, prior_gprc5d_yes_no,
         number_of_prior_lines_of_therapy_before_bs_ab_cat,
         number_of_prior_lines_of_therapy_before_bs_ab, prior_auto_sct_no_0_yes_1, 
         
         time_most_recent_bcma_to_initiation_days, time_last_gprc5d_to_initiation_days,
         prophylactic_tocilizumab_n_0_y_1,
         ) %>%
  tbl_summary(by = prophylactic_tocilizumab_n_0_y_1,
              type = list(#c(days_of_icu_admission) ~ "continuous",
                          c(all_continuous()) ~ "continuous2",
                          c(all_dichotomous()#, -male_sex
                            ) ~ "categorical"),
              statistic = list(c(all_continuous2()) ~ c(
                "{mean} ({sd})",
                "{median} ({p25}, {p75})",
                "{min}, {max}")), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_spanning_header(all_stat_cols() ~ "Prophylactic Tocilizumab") %>% 
  remove_footnote_header(columns = everything()) %>% as_gt()
```

## Table AE
```{r Table 6}
bsab_data %>% 
  select(max_crs_grade_0_5, crs_any, 
         crs_gradecat2, gr2_crs, 
         crs_gradecat3, gr3_crs, 
         duration_of_crs_days, 
         recurrent_crs_n_0_y_1, 
         day_of_onset_crs_relative_to_initiation_days, 
         day_of_max_crs_relative_to_initiation, 
         crs_14d, crs_30d, max_crs_grade_d14, max_crs_grade_d30, recurrent_crs_d14, recurrent_crs_d30, time_onset_crs_to_initiation_cat,
         max_icans_grade, icans_any, 
         icans_gradecat2, gr2_icans, 
         icans_gradecat3, gr3_icans, 
         duration_of_icans_days,
         day_of_onset_icans_relative_to_initiation_days, day_of_max_icans_grade_relative_to_initiation,
         icans_14d, icans_30d, max_icans_grade_d14, max_icans_grade_d30, time_onset_icans_to_initiation_cat,
         concurent_crs_icans_d14,
         
         
         bs_ab_sud_inpatient_0_bs_ab_sup_outpatient_1,
         prophylactic_tocilizumab_n_0_y_1) %>%
  tbl_summary(by = prophylactic_tocilizumab_n_0_y_1,
              type = list(
                c(duration_of_crs_days, duration_of_icans_days) ~ "continuous",#, 
                #     day_of_onset_crs_relative_to_initiation_days,
                #     day_of_max_crs_relative_to_initiation,
                #     day_of_onset_icans_relative_to_initiation_days, 
                #     day_of_max_icans_grade_relative_to_initiation) ~ "continuous",
                all_dichotomous() ~ "categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_spanning_header(all_stat_cols() ~ "Prophylactic Tocilizumab") %>% 
  remove_footnote_header(columns = everything()) %>% as_gt()
```

## Table Infections
```{r table Infections}
bsab_data %>%
  select(any_infection, any_sevinfection,
         time_from_bsab_therapy_to_1st_infection_days,
         number_of_infections, 
         infection_type_1, infection_severity_1,
         infection_type_2, infection_severity_2,
         infection_type_3, infection_severity_3,
         infection_type_4, infection_severity_4,
         infection_type_d30,
         
         
         prophylactic_tocilizumab_n_0_y_1) %>%
  
  tbl_summary(by = prophylactic_tocilizumab_n_0_y_1,
              # label = list(any_severe_infection = "Any severe infection",
              #              total_number_of_infection = "Total number of infections",
              #              infection_type = "Infection type"),
              type = list(c(number_of_infections) ~ "continuous",
                          all_dichotomous() ~ "categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
              digits = all_continuous() ~ 1
  ) %>%
  bold_labels() %>% add_stat_label() %>%
    add_p() %>% bold_p(t = 0.05) %>% add_overall() %>%
  modify_spanning_header(all_stat_cols() ~ "Prophylactic Tocilizumab") %>% 
  remove_footnote_header(columns = everything())

# long_infection_data <- bsab_data %>%
#   select(patient_identifier, #date_of_bs_ab_step_up_d1,
#          time_from_bsab_therapy_to_1st_infection_days,
#          time_from_bsab_therapy_to_1st_infection_months,
#          pfs_time_from_initiation_months,
#          pathogen,
#          any_infection, #number_of_infections,
#          infection_type_1, infection_severity_1,
#          infection_type_2, infection_severity_2,
#          infection_type_3, infection_severity_3,
#          infection_type_4, infection_severity_4,
#          prophylactic_tocilizumab_n_0_y_1) %>%
#   mutate(pathogen_count = sapply(strsplit(pathogen, ","), length)) %>% 
#   separate_wider_delim(cols = pathogen, delim = ", ",
#                        names = c(paste("pathogen_", 1:max(.$pathogen_count), sep = "")), 
#                        too_few = "align_start", too_many = "error", 
#                        cols_remove = TRUE) %>% 
#   mutate(across(c(contains("pathogen")), ~ str_to_sentence(.))) %>% 
#   mutate(across(c(contains("pathogen")), ~ trimws(.))) %>% 
#   # `colnames<-`(str_remove(
#   #   colnames(.),
#   #   "bacterial_viral_fungal|_severe_hospitalization_or_requiring_iv_antibiotics") %>%
#   #     str_replace(., "number_", "type_")) %>%
#   pivot_longer(cols = -c(patient_identifier, #date_of_bs_ab_step_up_d1,
#                          prophylactic_tocilizumab_n_0_y_1, time_from_bsab_therapy_to_1st_infection_days,
#                          time_from_bsab_therapy_to_1st_infection_months,
#                          pfs_time_from_initiation_months,
#                          infection_n_0_y_1#, number_of_infections
#                          ),
#                names_pattern = "(pathogen_|infection_type_|infection_severity_)(1|2|3|4).*",
#                names_to = c(".value", "sequence")) %>% 
#   mutate(infection_severity_ = case_when(
#     infection_severity_ == "Mild"          ~ NA_character_,
#     TRUE                                   ~ infection_severity_
#   )) %>%
#   rename(any_severe_infection = infection_severity_,
#          any_infection = infection_n_0_y_1,
#          infection_type = infection_type_) %>% 
#   filter(!is.na(infection_type) | !is.na(any_severe_infection) | sequence == 1) %>% 
#   group_by(patient_identifier) %>%
#   mutate(total_number_of_infection = case_when(
#     !is.na(infection_type) |
#       !is.na(any_severe_infection)        ~ n()
#   )) %>%
#   arrange(patient_identifier, sequence, infection_type) %>% 
#   ungroup()
# 
# # wide_infection_data <-
# long_infection_data %>%
#   # Only need to know if patient got at least 1 severe
#   group_by(patient_identifier) %>%
#   fill(any_severe_infection, .direction = "updown") %>%
#   ungroup() %>% 
#   mutate(any_severe_infection = case_when(
#     any_severe_infection == "Severe"              ~ "Yes",
#     !is.na(any_infection)                         ~ "No"
#   )) %>%
#   select(-sequence, -pathogen_) %>%
#   distinct() %>%
#   group_by(patient_identifier, 
#            time_from_bsab_therapy_to_1st_infection_days,
#            time_from_bsab_therapy_to_1st_infection_months,
#            pfs_time_from_initiation_months,
#            prophylactic_tocilizumab_n_0_y_1,
#            total_number_of_infection, any_severe_infection,
#            any_infection) %>%
#   
#   summarise_at(vars(infection_type),
#                str_c, collapse = "; ") %>%
#   ungroup() %>%
#   # mutate(str_count = sapply(strsplit(infection_type, "; "), length), .before = 5) %>%
# 
# # # mutate(time_from_bsab_therapy_to_infection_days = interval(
# #   #   start = date_of_bs_ab_step_up_d1,
# #   #   end = date_of_infection_)/
# #   #     duration(n=1, units = "days"))
# #   mutate()
# #   mutate(any_severe_infection = case_when(
# #     infection_severity_ == "Severe"              ~ "Yes",
# #     !is.na(infection_n_0_y_1)                    ~ "No"
# #   ), .after = infection_n_0_y_1) %>%
#   select(any_infection, any_severe_infection,
#          time_from_bsab_therapy_to_1st_infection_days,
#          total_number_of_infection,
#          infection_type,
#          prophylactic_tocilizumab_n_0_y_1) %>%
# 
#   tbl_summary(by = prophylactic_tocilizumab_n_0_y_1,
#               label = list(any_severe_infection = "Any severe infection",
#                            total_number_of_infection = "Total number of infections",
#                            infection_type = "Infection type"),
#               type = list(all_dichotomous() ~ "categorical"),
#               statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
#               digits = all_continuous() ~ 1
#   ) %>%
#   bold_labels() %>% add_stat_label() %>%
#     add_p() %>% bold_p(t = 0.05) %>% add_overall() %>%
#   modify_spanning_header(all_stat_cols() ~ "Prophylactic Tocilizumab") %>% 
#   remove_footnote_header(columns = everything()) %>% as_gt()



# bsab_data %>%
#   select(patient_identifier,
#          infection_n_0_y_1, number_of_infections,
#          infection_1_type,
#          infection_severity_1st_severe_hospitalization_or_requiring_iv_antibiotics, time_from_bsab_therapy_to_1st_infection_days,
#          infection_2_type,
#          infection_severity_2nd_severe_hospitalization_or_requiring_iv_antibiotics,
#          infection_3_type,
#          infection_severity_3rd_severe_hospitalization_or_requiring_iv_antibiotics,
#          infection_4_type,
#          infection_severity_4th_severe_hospitalization_or_requiring_iv_antibiotics,
#          prophylactic_tocilizumab_n_0_y_1) %>%
#   mutate(any_severe_infection = case_when(
#     if_any(any_of(contains("infection_severity")), ~ str_detect(.x, "Severe")) ~ "Yes",
#     !is.na(infection_n_0_y_1) ~ "No"
#   ), .after = infection_n_0_y_1) %>%
#   select(-patient_identifier) %>%
#   tbl_summary(by = prophylactic_tocilizumab_n_0_y_1,
#               type = list(
#                 c(number_of_infections) ~ "categorical"),
#     statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
#     digits = all_continuous() ~ 1
#   ) %>%
#   bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall()
```

## Table 5. Responses
```{r Table 7}
bsab_data %>% 
  select(#day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, 
         # day30_response, 
         day30_response_v2, ORR_30days, 
         VGPRorbetter_30days, CRorbetter_30days, 
         #day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, 
         # mon3_response, 
         mon3_response_v2, ORR_mon3, 
         VGPRorbetter_mon3, CRorbetter_mon3, 
         best_response, best_VGPRorbetter, 
         best_CRorbetter, best_ORRcollapsed, 
         # ORR_as_best_response, 
         # best_response_s_cr_cr_vgpr_pr_mr_sd_pd, 
         # best_response_mrd_flow_positive_vs_negative, 
         # best_response_mrd_clonoseq_positive_vs_negative,
         best_MRD_response, best_response_CR_MRD,
         prophylactic_tocilizumab_n_0_y_1) %>%
  tbl_summary(by = prophylactic_tocilizumab_n_0_y_1,
              type = list(all_dichotomous() ~ "categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_spanning_header(all_stat_cols() ~ "Prophylactic Tocilizumab") %>% 
  remove_footnote_header(columns = everything()) %>% as_gt()
```

## Table 6. Clinical outcomes
```{r Table 8}
bsab_data %>% 
  select(progression_yes_no, pfs_event, pfs_time_from_initiation_months, 
         death_yes_no, os_event, 
         os_time_from_initiation_months, 
         prophylactic_tocilizumab_n_0_y_1) %>%
  tbl_summary(by = prophylactic_tocilizumab_n_0_y_1,
              type = list(all_dichotomous() ~ "categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_spanning_header(all_stat_cols() ~ "Prophylactic Tocilizumab") %>% 
  remove_footnote_header(columns = everything()) %>% as_gt()

bsab_data %>% 
  select(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain,
         prophylactic_tocilizumab_n_0_y_1) %>%
  tbl_summary(by = prophylactic_tocilizumab_n_0_y_1) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_spanning_header(all_stat_cols() ~ "Prophylactic Tocilizumab") %>% 
  remove_footnote_header(columns = everything()) %>% as_gt()
```

## Table 7. Post BiTe therapy related information
```{r}
bsab_data %>% 
  select("Progression with EMD on BiTe" = progression_with_emd_on_bi_te,
         "Bone marrow plasma cell percent at PD on BiTe" = bone_marrow_plasma_cell_percent_at_pd_on_bi_te,
         "CRP (mg/dl)l at PD on BiTe" = crp_mg_d_l_at_pd_on_bi_te,
         "LDH (ul) at PD on BiTe" = ldh_u_l_at_pd_on_bi_te,
         "Ferritin (ng/ml) at PD on BiTe" = ferritin_ng_m_l_at_pd_on_bi_te,
         
         "best response to treatment number 1 after post BiTe progression" = best_response_to_treatment_number_1_after_post_bi_te_progression,
         # date_of_pd_to_treatment_number_1_after_post_bi_te_progression,
         "progression with EMD on 1st treatment post BiTe" = progression_with_emd_on_1st_treatment_post_bi_te,
         "Bone marrow plasma cell percent at PD on 1st treatment post BiTe" = bone_marrow_plasma_cell_percent_at_pd_on_1st_treatment_post_bi_te,
         "CRP (mg/dl)l_at_pd_on_1st treatment post BiTe" = crp_mg_d_l_at_pd_on_1st_treatment_post_bi_te,
         ldh_u_l_at_pd_on_1st_treatment_post_bi_te = ldh_u_l_at_pd_on_1st_treatment_post_bi_te,
         "Ferritin (ng/ml)_at_pd_on_1st treatment post BiTe" = ferritin_ng_m_l_at_pd_on_1st_treatment_post_bi_te,
         
         "best response to treatment number 2 after post BiTe progression" = best_response_to_treatment_number_2_after_post_bi_te_progression,
         # date_of_pd_to_treatment_number_2_after_post_bi_te_progression,
         "progression with EMD on 2nd_treatment_post_bi_te" = progression_with_emd_on_2nd_treatment_post_bi_te,
         "Bone marrow plasma cell percent at PD on 2nd_treatment_post_bi_te" = bone_marrow_plasma_cell_percent_at_pd_on_2nd_treatment_post_bi_te,
         "CRP (mg/dl)l at 2nd treatment post BiTe" = crp_mg_d_l_at_pd_on_2nd_treatment_post_bi_te,
         "LDH (ul) at 2nd treatment post BiTe" = ldh_u_l_at_pd_on_2nd_treatment_post_bi_te,
         "Ferritin (ng/ml) at 2nd treatment post BiTe" = ferritin_ng_m_l_at_pd_on_2nd_treatment_post_bi_te,

         prophylactic_tocilizumab_n_0_y_1) %>%
  tbl_summary(by = prophylactic_tocilizumab_n_0_y_1,
              type = list(c("Bone marrow plasma cell percent at PD on 1st treatment post BiTe",
                            "CRP (mg/dl)l_at_pd_on_1st treatment post BiTe",
                            "Bone marrow plasma cell percent at PD on 2nd_treatment_post_bi_te",
                            "CRP (mg/dl)l at 2nd treatment post BiTe",
                            "LDH (ul) at 2nd treatment post BiTe",
                            "Ferritin (ng/ml) at 2nd treatment post BiTe"
                            ) ~ "continuous",
                          all_dichotomous() ~ "categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous2() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_spanning_header(all_stat_cols() ~ "Prophylactic Tocilizumab") %>% 
  remove_footnote_header(columns = everything()) %>% as_gt()
```




# Survival

## OS
Median OS in months
```{r}
survfit(Surv(time = bsab_data$os_time_from_initiation_months,
                   event = bsab_data$os_event) ~ 1,
              data = bsab_data) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median survival (95% CI)**"
  ) %>% add_nevent() %>% add_n()
survfit(Surv(time = bsab_data$os_time_from_initiation_months,
                   event = bsab_data$os_event) ~ prophylactic_tocilizumab_n_0_y_1,
              data = bsab_data) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median survival (95% CI)**"
  ) %>% add_nevent() %>% add_n()

list(
  survfit(Surv(time = bsab_data$os_time_from_initiation_months,
               event = bsab_data$os_event) ~ 1,
          data = bsab_data),
  survfit(Surv(time = bsab_data$os_time_from_initiation_months,
               event = bsab_data$os_event) ~ prophylactic_tocilizumab_n_0_y_1,
          data = bsab_data)
) %>%
  tbl_survfit(times = c(6, 12),
              label_header = "**OS Rate at {time} Months**")
```

```{r KM OS, fig.height=6}
ggsurvplot(survfit(Surv(os_time_from_initiation_months, os_event) ~ prophylactic_tocilizumab_n_0_y_1,
                   data=bsab_data),
           font.main = c(20, "bold", "black"),
           font.x = c(12, "plain", "black"),
           font.y = c(12, "plain", "black"),
           font.legend = c(10, "plain", "black"),
           font.tickslab = c(10, "plain", "black"),
           size = 1.5,

           xlab = "Time (months)",
           ylab = "OS (probability)",
           legend = "top", legend.title = "", 
           # legend.labs = c("", ""),
           pval = TRUE, pval.size = 4, 
           conf.int = FALSE,
           risk.table = TRUE,
           risk.table.fontsize = 4,
           tables.y.text = FALSE,
           tables.theme = theme_classic()+
             theme(text = element_text(size = 10),
                   # plot.title = element_text(size = 10),  # Table title ("Number at risk")
                   axis.text.x = element_text(size = 10),                # Time ticks (x-axis)
                   axis.title.x = element_text(size = 12)                # X-axis label ("Time")
             ),
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 2))
```



## PFS
Median PFS in months
```{r}
survfit(Surv(time = bsab_data$pfs_time_from_initiation_months,
                   event = bsab_data$pfs_event) ~ 1,
              data = bsab_data) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median PFS (95% CI)**"
  ) %>% add_nevent() %>% add_n()
survfit(Surv(time = bsab_data$pfs_time_from_initiation_months,
                   event = bsab_data$pfs_event) ~ prophylactic_tocilizumab_n_0_y_1,
              data = bsab_data) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median PFS (95% CI)**"
  ) %>% add_nevent() %>% add_n()

list(
  survfit(Surv(time = bsab_data$pfs_time_from_initiation_months,
               event = bsab_data$pfs_event) ~ 1,
          data = bsab_data),
  survfit(Surv(time = bsab_data$pfs_time_from_initiation_months,
               event = bsab_data$pfs_event) ~ prophylactic_tocilizumab_n_0_y_1,
          data = bsab_data)
) %>%
  tbl_survfit(times = c(6, 12),
              label_header = "**PFS Rate at {time} Months**")
```

```{r KM PFS, fig.height=6}
ggsurvplot(survfit(Surv(pfs_time_from_initiation_months, pfs_event) ~ prophylactic_tocilizumab_n_0_y_1,
                   data=bsab_data),
           font.main = c(20, "bold", "black"),
           font.x = c(12, "plain", "black"),
           font.y = c(12, "plain", "black"),
           font.legend = c(10, "plain", "black"),
           font.tickslab = c(10, "plain", "black"),
           size = 1.5,

           xlab = "Time (months)",
           ylab = "PFS (probability)",
           legend = "top", legend.title = "",
           # legend.labs = c("", ""),
           pval = TRUE, pval.size = 4,
           conf.int = FALSE,
           risk.table = TRUE,
           risk.table.fontsize = 3,
           tables.y.text = FALSE,
           tables.theme = theme_classic()+
             theme(text = element_text(size = 10),
                   # plot.title = element_text(size = 10),  # Table title ("Number at risk")
                   axis.text.x = element_text(size = 10),                # Time ticks (x-axis)
                   axis.title.x = element_text(size = 12)                # X-axis label ("Time")
             ),
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 2))
```


# NRM
NRM is defined as death unrelated to Multiple Myeloma; therefore, any death occurring after disease progression (PD) is classified as non-NRM.
```{r, fig.height=6}
nrm_curves <- bsab_data %>% 
  mutate(nrm_response = case_when(
    os_event == 0                        ~ 0,
    
    os_event == 1 &
      str_detect(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain, "1|PD|mm")
                                         ~ 0,# 0
    os_event == 1 &
      !is.na(date_of_pd)                 ~ 0,# 0
    
    
    os_event == 1                        ~ 1
  )) #%>% 
  # select(patient_identifier, os_event, os_time_from_initiation_months, nrm_response,
  #        date_of_last_contact, date_of_pd, cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain)

ggsurvplot(survfit(Surv(os_time_from_initiation_months, nrm_response) ~ prophylactic_tocilizumab_n_0_y_1,
                   data=nrm_curves),
           fun = "event",
           font.main = c(20, "bold", "black"),
           font.x = c(12, "plain", "black"),
           font.y = c(12, "plain", "black"),
           font.legend = c(10, "plain", "black"),
           font.tickslab = c(10, "plain", "black"),
           size = 1.5,
           surv.median.line = "hv",

           xlab = "Time (months)",
           ylab = "Cumulative Incidence of NRM",
           legend = "top", legend.title = "",
           # legend.labs = c("", "", ""),
           pval = TRUE, pval.size = 4,
           conf.int = FALSE,
           risk.table = TRUE,
           risk.table.fontsize = 3,
           tables.y.text = FALSE,
           tables.theme = theme_classic()+
             theme(text = element_text(size = 10),
                   # plot.title = element_text(size = 10),  # Table title ("Number at risk")
                   axis.text.x = element_text(size = 10),                # Time ticks (x-axis)
                   axis.title.x = element_text(size = 12)                # X-axis label ("Time")
             ),
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 2))
```










